---
title: "PERMA CFA Youth"
author: "Levi Brackman"
date: "December 4th 2015"
output: html_document
---

##Analysis with only the five PERMA constructs

From Julie Butler and Peggy Kerns PERMA & EPOCH

* 514 of these cases onl answered 17 of the questions done on an online study using Qualtrics participents
* 239 answered all 23 questions from students at tow sydney schools one private and one public
* Below is two analysis one with complete cases and one with all the data and therefore imputed

#Items

1. In general, to what extent do you lead a purposeful and meaningful life? (only in 239 of the questions)
2. How much of the time do you feel you are making progress towards accomplishing your goals? (only in 239 of the questions)
3. How often do you become absorbed in what you are doing? (only in 239 of the questions)
4. In general, how would you say your health is? (only in 239 of the questions)
5. In general, how often do you feel joyful?
6. To what extent do you receive help and support from others when you need it?
7. In general, how often do you feel anxious
8. How often do you achieve the important goals you have set for yourself?
9. In general, to what extent do you feel that what you do in your life is valuable and worthwhile?
10. In general, how often do you feel positive?
11. In general, to what extent do you feel excited and interested in things?
12. How lonely do you feel in your daily life?
13. How satisfied are you with your current physical health? (only in 239 of the questions)
14. In general, how often do you feel angry?
15. To what extent have you been feeling loved?
16. How often are you able to handle your responsibilities?
17. To what extent do you generally feel you have a sense of direction in your life?
18. Compared to others of your same age and sex, how is your health? (only in 239 of the questions)
19. How satisfied are you with your personal relationships?
20. In general, how often do you feel sad?
21. How often do you lose track of time while doing something you enjoy?
22. In general, to what extent do you feel contented?
23. Taking all things together, how happy would you say you are?

```{r}
library(lavaan)
require(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
```
Loadthedata
```{r}
data <- read.csv("~/Git/stats/Perma_Study/PERMAfinal.csv")
```
Create Dataset with Coplete Cases
```{r}
data1 <- na.omit(data)
```
Create the model with 9 factors as the instrument was designed
```{r}
five.model= 'Acomplishment =~ PERMA_A1_1 + PERMA_A2_1 + PERMA_A3_1    
              Engagement =~ PERMA_E1_1 + PERMA_E2_1 + PERMA_E3_1   
              Positive Emotion =~ PERMA_P1_1 + PERMA_P2 + PERMA_P3_1 
              Relationship =~ PERMA_R1_1 + PERMA_R2_1 + PERMA_R3_1   
              Meaning =~ PERMA_M1_1 + PERMA_M2_1 + PERMA_M3_1'

```
Run the model with all data
```{r}
five.fit=cfa(five.model, data=data, missing="fiml")
```
Run the model with complete cases
```{r}
five.fit1=cfa(five.model, data=data1, missing = "fiml")
```
Create pictures with all data
```{r}
semPaths(five.fit, whatLabels = "std", layout = "tree")
```
Create pictures with all complet cases
```{r}
semPaths(five.fit1, whatLabels = "std", layout = "tree")
```
Summarie with all data
```{r}
summary(five.fit, standardized = TRUE, rsquare=TRUE)
```
Summarie with complete cases
```{r}
summary(five.fit1, standardized = TRUE, rsquare=TRUE)
```
Residual correlations with all data
```{r}
correl = residuals(five.fit, type="cor")
correl
```
Residual correlations with complete cases
```{r}
correl1 = residuals(five.fit1, type="cor")
correl1
```
Zscore correlation for all data anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels = residuals(five.fit, type = "standardized")
```
Zscore correlation for complete cases anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels1 = residuals(five.fit1, type = "standardized")
```
Modification indicies for all data
```{r}
modindices(five.fit, sort. = TRUE, minimum.value = 3.84)
```
Modification indicies for complet cases
```{r}
modindices(five.fit1, sort. = TRUE, minimum.value = 3.84)
```
Fit Measures for all data
```{r}
fitmeasures(five.fit)
```
Fit Measures for complate cases
```{r}
fitmeasures(five.fit1)
```
Create dataset for Target rotation for all data
```{r}
PermaTR<-select(data, PERMA_P1_1,  PERMA_P2,  PERMA_P3_1, PERMA_E1_1, PERMA_E2_1, PERMA_E3_1, PERMA_R1_1,  PERMA_R2_1,   PERMA_R3_1, PERMA_M1_1, PERMA_M2_1,  PERMA_M3_1, PERMA_A1_1, PERMA_A2_1, PERMA_A3_1)
colnames(PermaTR) <- c("1","2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15")
PermaTR<-tbl_df(PermaTR)
PermaTR
```
Target Rotation for all 753 cases
```{r}
Targ_key <- make.keys(15,list(f1=1:3,f2=4:6, f3=7:9, f4=10:12, f5=13:15))
```
fix the 0s, allow the NAs to be estimated
```{r}
Targ_key <- scrub(Targ_key,isvalue=1)  
Targ_key <- list(Targ_key)
```
convert the raw data to correlation matrix uisng FIML
```{r}
Perma_cor <- corFiml(PermaTR) 
```
TargetT for orthogonal rotation
```{r}
out_targetQ <- fa(Perma_cor,5,rotate="TargetQ", n.obs = 753, Target=Targ_key) 
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
Complete 239 cases
```{r}
PermaTR<-select(data1, PERMA_P1_1,  PERMA_P2,  PERMA_P3_1, PERMA_E1_1, PERMA_E2_1, PERMA_E3_1, PERMA_R1_1,  PERMA_R2_1,   PERMA_R3_1, PERMA_M1_1, PERMA_M2_1,  PERMA_M3_1, PERMA_A1_1, PERMA_A2_1, PERMA_A3_1)
colnames(PermaTR) <- c("1","2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15")
PermaTR<-tbl_df(PermaTR)
PermaTR
```
#Target Roratation for complete cases
```{r}
Targ_key <- make.keys(15,list(f1=1:3,f2=4:6, f3=7:9, f4=10:12, f5=13:15))
```
fix the 0s, allow the NAs to be estimated
```{r}
Targ_key <- scrub(Targ_key,isvalue=1)  
Targ_key <- list(Targ_key)
```
convert the raw data to correlation matrix uisng FIML
```{r}
Perma_cor <- corFiml(PermaTR)
```
TargetT for orthogonal rotation
```{r}
out_targetQ <- fa(Perma_cor,5,rotate="TargetQ", n.obs = 239, Target=Targ_key)
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```