---
title: "CFA ASDQII"
author: "Levi Brackman"
date: "23 July 2015"
output: html_document
---
ASDQII
Please select from the list below how true or untrue each item is / for you. 

1. I get good grades in ENGLISH LANGUAGE classes.	(English)
2. Work in ENGLISH LANGUAGE classes is easy for me.	(English)
3. I learn things quickly in ENGLISH LANGUAGE classes.	P (English)
4. Compared to others my age I am good at ENGLISH LANGUAGE classes.	(English)
5. I have always done well in ENGLISH LANGUAGE classes.	P (English)

6. I learn things quickly in MATHEMATICS classes.	(Math)
7. I have always done well in MATHEMATICS classes.	(Math)
8. Compared to others my age I am good at MATHEMATICS classes. (Math)	
9. Work in MATHEMATICS classes is easy for me.	(Math)
10. I get good grades in MATHEMATICS classes.	(Math)

11. I get good grades in SCIENCE classes.	(Science)
12. Work in SCIENCE classes is easy for me. (Science)
13. I learn things quickly in SCIENCE classes.(Science)	
14. Compared to others my age I am good at SCIENCE classes.	(Science)
15. I have always done well in SCIENCE classes.	(Science)

16. I have always done well in SCHOOL SUBJECTS classes.	(all subjects)
17. Compared to others my age I am good at SCHOOL SUBJECTS classes.	(all subjects)
18. I get good grades in SCHOOL SUBJECTS classes.	(all subjects)
19. Work in SCHOOL SUBJECTS classes is easy for me.	(all subjects)
20. I learn things quickly in SCHOOL SUBJECTS classes. (all subjects)

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
```
#loadthedata
```{r}
data <- read.csv("~/Psychometric_study_data/allsurveysYT1.csv")
data<-tbl_df(data)
ASDQII<-select(data, ASDQII_1, ASDQII_2, ASDQII_3, ASDQII_4, ASDQII_5, ASDQII_6, ASDQII_7, ASDQII_8, ASDQII_9, ASDQII_10, ASDQII_11,ASDQII_12, ASDQII_13, ASDQII_14, ASDQII_15, ASDQII_16, ASDQII_17, ASDQII_18, ASDQII_19, ASDQII_20)
ASDQII<-tbl_df(ASDQII)
ASDQII

```
#create plots
```{r}
#ggpairs(ASDQII, columns = 1:15, title="Big 5 Marsh" )

```
#create the models
```{r}
four.model= ' English  =~ ASDQII_1 +  ASDQII_2  + ASDQII_3 + ASDQII_4 + ASDQII_5   
              Math =~   ASDQII_6 + ASDQII_7 + ASDQII_8 + ASDQII_9  +ASDQII_10       
              Science =~      ASDQII_11 + ASDQII_12  +ASDQII_13 +  ASDQII_14 + ASDQII_15 
              All Subjects =~  ASDQII_16 + ASDQII_17 + ASDQII_18 + ASDQII_19 + ASDQII_20' 

one.model= 'ASDQII =~ ASDQII_1 +  ASDQII_2  + ASDQII_3 + ASDQII_4 + ASDQII_5 + ASDQII_6 + ASDQII_7 + ASDQII_8 + ASDQII_9 + ASDQII_10 + ASDQII_11 + ASDQII_12 + ASDQII_13 +  ASDQII_14 + ASDQII_15 + ASDQII_16 + ASDQII_17 + ASDQII_18 + ASDQII_19 + ASDQII_20 '
```
#run the models
```{r}
four.fit=cfa(four.model, data=ASDQII, missing = "fiml")
one.fit=cfa(one.model, data=ASDQII, missing = "fiml")
```

#create pictures
```{r}
semPaths(four.fit, whatLabels = "std", layout = "tree")
semPaths(one.fit, whatLabels = "std", layout = "tree")
```
#summaries
```{r}
summary(four.fit, standardized = TRUE, rsquare=TRUE)
summary(one.fit, standardized = TRUE, rsquare=TRUE)
```
#Residual correlations
```{r}
correl = residuals(four.fit, type="cor")
correl
View(correl$cor)
correl1 = residuals(one.fit, type="cor")
correl1
View(correl1$cor)
```
#zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels = residuals(four.fit, type = "standardized")
View(zcorrels$cov)
zcorrels1 = residuals(one.fit, type = "standardized")
View(zcorrels1$cov)
```
#Modification indicies
```{r}
modindices(four.fit, sort. = TRUE, minimum.value = 3.84)
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
```
#Fit Measures
```{r}
fitmeasures(four.fit)
fitmeasures(one.fit)
```
#Create dataset for Target rotation
```{r}
ASDQIITR<-select(data, ASDQII_1  , ASDQII_2 , ASDQII_3, ASDQII_4 ,  ASDQII_5 , ASDQII_6 ,ASDQII_7 , ASDQII_8 , ASDQII_9 , ASDQII_10 , ASDQII_11 , ASDQII_12 , ASDQII_13 , ASDQII_14 , ASDQII_15, ASDQII_16, ASDQII_17, ASDQII_18, ASDQII_19, ASDQII_20)
colnames(ASDQIITR) <- c("1","2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20")
#Target Roration
```{r}
Targ_key <- make.keys(20,list(f1=1:5,f2=6:10, f3=11:15, f4=16:10))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
ASDQIITR_cor<- corFiml(ASDQIITR)
out_targetQ <- fa(ASDQIITR_cor,4,rotate="TargetQ", n.obs = 670, Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
