---
title: "All Purpose Scales CFA TR"
author: "Levi Brackman"
date: "27 July 2015"
output: html_document
---

```{r}
##load packages
library(psych)
library(GPArotation)
library(plyr)
library(dplyr)
# data preparation
data <- read.csv("stats/allsurveysT1.csv")
purposescales<-select(data, PWB_1, PWB_2, PWB_3, PWB_4, PWB_5, PWB_6, PWB_7, PWB_8, PWB_9, APSI_1, APSI_2,  APSI_3,  APSI_4,  APSI_5,  APSI_6, APSI_7, APSI_8, LET_1, LET_2, LET_3,  LET_4,  LET_5,  LET_6, MLQ_1, MLQ_2, MLQ_3, MLQ_4, MLQ_5, MLQ_6,MLQ_7, MLQ_8, MLQ_9, MLQ_10)
purposescales$PWB_1  <-  7- purposescales$PWB_1
purposescales$PWB_2  <-  7- purposescales$PWB_2
purposescales$PWB_3  <-  7- purposescales$PWB_3
purposescales$PWB_4  <-  7- purposescales$PWB_4
purposescales$PWB_9  <-  7- purposescales$PWB_9
purposescales$MLQ_9  <-  8- purposescales$MLQ_9
purposescales$LET_1  <-  6- purposescales$LET_1
purposescales$LET_3  <-  6- purposescales$LET_3
purposescales$LET_5  <-  6- purposescales$LET_5
purposescales<- data.frame(apply(purposescales,2, as.numeric))
purposescales<-tbl_df(purposescales)
purposescales
str(purposescales)
colnames(purposescales) <- c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33")
#purposescales<- purposescales[complete.cases(purposescales[,]),]
##EFA
##number of factors
##parallal analysis and scree plot
parallel<-fa.parallel(purposescales, fm="ml",fa="fa")
#two factors are greater than one Eigenvalue scree plot says there are two factors. Paralel analysis suggests 4 factors
#eigenvalues (kaiser)
parallel$fa.values
#over 1=2, over .7=2
#doign aprincipal components analysis to see how many factors there might be using that method
#Deal with NA doing principle componant analysis
princomp(na.omit(purposescales), cor = TRUE)
parallel2<-princomp(na.omit(purposescales), cor = TRUE)
summary(parallel2)
plot(parallel2)##results show at least two factors
#simple structure
twofactor<-fa(purposescales, nfactors=2, rotate="oblimin", fm="ml")
twofactor
threefactor<-fa(purposescales, nfactors=3, rotate="oblimin", fm="ml")
threefactor
fourfactor<-fa(purposescales, nfactors=4, rotate="oblimin", fm="ml")
fourfactor
fivefactor<-fa(purposescales, nfactors=5, rotate="oblimin", fm="ml")
fivefactor
#1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33
 
#Create dataset for Target rotation
```{r}
all_surveys<-read.csv("allsurveysT1.csv")
purposescales<-select(all_surveys,  PWB_7, PWB_8, APSI_1, APSI_2, APSI_4,  APSI_5, APSI_7,  APSI_8, LET_2, LET_4, PWB_1,  PWB_2,  PWB_3,  PWB_4,  PWB_5,  PWB_6,  PWB_9, APSI_3, APSI_6,  LET_1, LET_3,    LET_5,  LET_6, MLQ_9,  MLQ_2, MLQ_3, MLQ_7, MLQ_8,MLQ_10,    MLQ_1, MLQ_4, MLQ_5, MLQ_6)
purposescales$PWB_1  <-  7- purposescales$PWB_1
purposescales$PWB_2  <-  7- purposescales$PWB_2
purposescales$PWB_3  <-  7- purposescales$PWB_3
purposescales$PWB_4  <-  7- purposescales$PWB_4
purposescales$PWB_9  <-  7- purposescales$PWB_9
purposescales$MLQ_9  <-  8- purposescales$MLQ_9
purposescales$LET_1  <-  6- purposescales$LET_1
purposescales$LET_3  <-  6- purposescales$LET_3
purposescales$LET_5  <-  6- purposescales$LET_5
purposescales<- data.frame(apply(purposescales,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

purposescales<-tbl_df(purposescales)
purposescales
str(purposescales)
colnames(purposescales) <- c("1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19","20","21","22","23","24","25","26","27","28","29","30","31","32","33")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be purposescales
Targ_key <- make.keys(33,list(f1=1:10,f2=11:24, f3=25:29,f4=30:33))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(purposescales,4,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```


Our Father, our King, accept our prayer with mercy and with favor. 
Our Father, our King, open the gates of heaven to our prayer. 
Our Father, our King, let it be remembered that we are but dust. 
Our Father, our King, we beseech You, do not turn us away from You empty-handed. 
Our Father, our King, may this hour be an hour of mercy and a time of favor before You. 
Our Father, our King, have compassion upon us, and upon our infants and children. 
Our Father, our King, do it for the sake of those who were slain for Your holy Name. 
Our Father, our King, do it for the sake of those who were slaughtered for Your Oneness. 
Our Father, our King, do it for the sake of those who went through fire and water for the sanctification of Your Name. 
Our Father, our King, avenge the spilled blood of Your servants. 
Our Father, our King, do it for Your sake, if not for ours. 
Our Father, our King, do it for Your sake, and deliver us. 
Our Father, our King, do it for the sake of Your abounding mercies. 
Our Father, our King, do it for the sake of Your great, mighty and awesome Name which is proclaimed over us. 
Our Father, our King, be gracious to us and answer us, for we have no meritorious deeds; deal charitably and kindly with us and deliver us. 

