---
title: "MLQ and APSI EFA and CFA"
author: "Levi Brackman"
date: "March 16, 2016"
output: html_document
---

```{r}
##load packages
library(psych)
library(GPArotation)
library(plyr)
library(dplyr)
library(lavaan)
library(semPlot)
# data preparation
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
purposescales<-select(data, APSI_1, APSI_2,  APSI_4,  APSI_5, APSI_7, APSI_8,MLQ_1, MLQ_4, MLQ_5, MLQ_6, MLQ_9)


purposescales$MLQ_9  <-  8- purposescales$MLQ_9

purposescales<- data.frame(apply(purposescales,2, as.numeric))
purposescales<-tbl_df(purposescales)
purposescales
str(purposescales)

allpurpose_cor <- corFiml(purposescales)#uses FIML for missing data
purposescales<- purposescales[complete.cases(purposescales[,]),]
##EFA
##number of factors
##parallal analysis and scree plot
parallel<-fa.parallel(allpurpose_cor, n.obs=1288, fm="ml")
#three factors are greater than one Eigenvalue scree plot says there are three factors. 
#Paralel analysis suggests 6 factors
#eigenvalues (kaiser)
parallel$fa.values
#over 1=3, over .7=4
#doign aprincipal components analysis to see how many factors there might be using that method
#Deal with NA doing principle componant analysis
princomp(na.omit(allpurpose_cor), cor = TRUE)
parallel2<-princomp(na.omit(allpurpose_cor), cor = TRUE)
summary(parallel2)
plot(parallel2)##results show at least two factors
#simple structure
onefactor<-fa(allpurpose_cor, nfactors=1, rotate="oblimin", fm="ml")
onefactor
#CFI
1-((twofactor$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))
fa2latex(fa(allpurpose_cor,2,n.obs=1288, rotate="oblimin", fm="ml"),heading="2f")
fa2latex(fa(allpurpose_cor,3,n.obs=1288, rotate="oblimin", fm="ml"),heading="3f")
fa2latex(fa(allpurpose_cor,4,n.obs=1288, rotate="oblimin", fm="ml"),heading="4f")
fa2latex(fa(allpurpose_cor,5,n.obs=1288, rotate="oblimin", fm="ml"),heading="5f")
fa2latex(fa(allpurpose_cor,6,n.obs=1288, rotate="oblimin", fm="ml"),heading="6f")


```
twofactor<-fa(allpurpose_cor, nfactors=2, n.obs=1288,  rotate="oblimin", fm="ml")
twofactor
#CFI
1-((twofactor$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))



```
Now let's do a CFE
```{r}
onefactor.model = 'Purpose =~ APSI_1 + APSI_2 + APSI_4 + APSI_5 + APSI_7 + APSI_8 + MLQ_1 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_9'
             
                
onefactor.fit=cfa(onefactor.model, data=purposescales, missing = "fiml")
semPaths(onefactor.fit, whatLabels = "std", layout = "tree")
summary(onefactor.fit, standardized = TRUE, rsquare=TRUE)
modindices(onefactor.fit, sort. = TRUE, minimum.value = 3.84)
fitmeasures(onefactor.fit)
```
Now let's do a CFE with MLQ and APSI as two factors.
```{r}

twofactor.model = 'APSI =~ APSI_1 + APSI_2 + APSI_4 + APSI_5 + APSI_7 + APSI_8
MLQ=~MLQ_1 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_9'
             
                
twofactor.fit=cfa(twofactor.model, data=purposescales, missing = "fiml")
semPaths(twofactor.fit, whatLabels = "std", layout = "tree")
summary(twofactor.fit, standardized = TRUE, rsquare=TRUE)
modindices(twofactor.fit, sort. = TRUE, minimum.value = 3.84)
fitmeasures(twofactor.fit)
```
```
Now let's do a CFE with MLQ and APSI as a bi-factor - fit does not get much better.
```{r}

bifactor.model = 'APSI =~ APSI_1 + APSI_2 + APSI_4 + APSI_5 + APSI_7 + APSI_8
MLQ=~MLQ_1 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_9
                           Purpose =~ APSI + MLQ'

             
                
bifactor.fit=cfa(bifactor.model, data=purposescales, missing = "fiml", std.lv = T)
semPaths(bifactor.fit, whatLabels = "std", layout = "tree")
summary(bifactor.fit, standardized = TRUE, rsquare=TRUE)
modindices(bifactor.fit, sort. = TRUE, minimum.value = 3.84)
fitmeasures(bifactor.fit)
```
Target Rotation ONE FACTOR
```{r}
purposescales<-tbl_df(purposescales)
purposescales
str(purposescales)
colnames(purposescales) <- c("1","2","3","4","5","6","7","8","9","10", "11")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be purposescales
Targ_key <- make.keys(11,list(f1=1:11))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
purposescales_cor <- corFiml(purposescales)
out_targetQ <- fa(purposescales_cor,1,rotate="TargetQ", n.obs = 1288, Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
fa2latex(fa(purposescales_cor,4,rotate="TargetQ", n.obs = 1288, Target=Targ_key),heading="Table 7 Factor Based on theory")
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
Target Rotation Two factors
```{r}
purposescales<-tbl_df(purposescales)
purposescales
str(purposescales)
colnames(purposescales) <- c("1","2","3","4","5","6","7","8","9","10","11")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be purposescales
Targ_key <- make.keys(11,list(f1=1:5,f2=6:11))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
purposescales_cor <- corFiml(purposescales)
out_targetQ <- fa(purposescales_cor,2,rotate="TargetQ", n.obs = 1288, Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
fa2latex(fa(purposescales_cor,4,rotate="TargetQ", n.obs = 1288, Target=Targ_key),heading="Table 7 Factor Based on theory")
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
```
Droping LQ 9 (negative worded question)
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
purposescales1<-select(data, APSI_1, APSI_2,  APSI_4,  APSI_5, APSI_7, APSI_8,MLQ_1, MLQ_4, MLQ_5, MLQ_6)
purposescales1<-tbl_df(purposescales1)
str(purposescales1)
colnames(purposescales1) <- c("1","2","3","4","5","6","7","8","9","10")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal #rotation based on what paper says facotrs should be purposescales
Targ_key <- make.keys(10,list(f1=1:10))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
purposescales_cor <- corFiml(purposescales1)
out_targetQ <- fa(purposescales_cor,1,rotate="TargetQ", n.obs = 1288, Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
fa2latex(fa(purposescales_cor,4,rotate="TargetQ", n.obs = 1288, Target=Targ_key),heading="Table 7 Factor Based on theory")
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
```
Now let's look at this as a bifactor model
```{r}

bifactor.model = 'Definate =~ APSI_2 + APSI_4 +  PWB_8 + APSI_7 + APSI_8 +  APSI_5 +  APSI_1 + LET_2
                Tend   =~ PWB_2 + PWB_9 + PWB_3 + PWB_5 + LET_1 + APSI_6
              MLQP =~ MLQ_4 + MLQ_5 + MLQ_6 + MLQ_1
              MLQS =~ MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8 + MLQ_10
                Definate ~~ 0*Tend
                Definate ~~ 0*MLQP
                Definate~~0*MLQS
                MLQP~~0*Tend
                MLQP~~0*MLQS
                MLQS~~0*Tend'
                
bifactor.fit=cfa(bifactor.model, data=all_surveys, missing = "fiml", std.lv = T)
semPaths(bifactor.fit, whatLabels = "std", layout = "tree")
summary(bifactor.fit, standardized = TRUE, rsquare=TRUE)
modindices(bifactor.fit, sort. = TRUE, minimum.value = 3.84)
fitmeasures(bifactor.fit)

bifactor1.model = 'Definate =~ APSI_2 + APSI_4 +  PWB_8 + APSI_7 + APSI_8 +  APSI_5 +  APSI_1 + LET_2
                Tend   =~ PWB_2 + PWB_9 + PWB_3 + PWB_5 + LET_1 + APSI_6
              MLQP =~ MLQ_4 + MLQ_5 + MLQ_6 + MLQ_1
              MLQS =~ MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8 + MLQ_10
              Purpose =~ APSI_2 + APSI_4 +  PWB_8 + APSI_7 + APSI_8 +  APSI_5 +  APSI_1 + LET_2 + PWB_2 + PWB_9 + PWB_3 + PWB_5 + LET_1 + APSI_6 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_1 + MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8 + MLQ_10'
              
              bifactor1.fit=cfa(bifactor1.model, data=all_surveys, missing = "fiml", std.lv = T)
semPaths(bifactor1.fit, whatLabels = "std", layout = "tree")
summary(bifactor1.fit, standardized = TRUE, rsquare=TRUE)
###modindices(bifactor1.fit, sort. = TRUE, minimum.value = 3.84)
fitmeasures(bifactor1.fit)
```
see whether purpose scales corrolate with ADSQII
```{r}

Corrolation = 'Definate =~ APSI_2 + APSI_4 +  PWB_8 + APSI_7 + APSI_8 +  APSI_5 +  APSI_1 + LET_2
                Tend   =~ PWB_2 + PWB_9 + PWB_3 + PWB_5 + LET_1 + APSI_6
              MLQP =~ MLQ_4 + MLQ_5 + MLQ_6 + MLQ_1
              MLQS =~ MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8 + MLQ_10
              English =~ ASDQII_1 + ASDQII_2 + ASDQII_3 + ASDQII_4 + ASDQII_5 
              Math =~ ASDQII_6 + ASDQII_7 + ASDQII_8 + ASDQII_9 + ASDQII_10              
              Science =~ ASDQII_11 + ASDQII_12 + ASDQII_13 + ASDQII_14 + ASDQII_15
              General =~ ASDQII_16 + ASDQII_17 + ASDQII_18 + ASDQII_19 + ASDQII_20'
                  corrolation.fit=cfa(Corrolation, data=all_surveys, missing = "fiml", std.lv = T)
semPaths(corrolation.fit, whatLabels = "std", layout = "tree")
summary(corrolation.fit, standardized = TRUE, rsquare=TRUE)
modindices(corrolation.fit, sort. = TRUE, minimum.value = 3.84)
fitmeasures(corrolation.fit)
corolations<-(corrolation.fit)
fitted<-fitted(corrolation.fit)
```
See is APSI_6 (I don;t know where I fit in the world) is corrolated with APSI_2 and APSI_4 (3.	I have a firm sense of who I am. 
	I know what I want out of life.) -- it is not.
```{r}
cor(all_surveys$APSI_4, all_surveys$APSI_2, use  = "complete.obs")
?cor
with(all_surveys, cor(APSI_6, APSI_4))
```
Corrorlations
```{r}

second.corrolation = '  F1  =~ PWB_1 + PWB_3 + APSI_6 + LET_1 + LET_3 + LET_5 
                F2 =~   PWB_7 + PWB_8 +  APSI_2 + APSI_4 + APSI_7 + APSI_8
               MLQP =~ MLQ_4 + MLQ_5 + MLQ_6 + MLQ_1
              MLQS =~ MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8 + MLQ_10
              English =~ ASDQII_1 + ASDQII_2 + ASDQII_3 + ASDQII_4 + ASDQII_5 
              Math =~ ASDQII_6 + ASDQII_7 + ASDQII_8 + ASDQII_9 + ASDQII_10              
              Science =~ ASDQII_11 + ASDQII_12 + ASDQII_13 + ASDQII_14 + ASDQII_15
              General =~ ASDQII_16 + ASDQII_17 + ASDQII_18 + ASDQII_19 + ASDQII_20'

                 second.fit=cfa(second.corrolation, data=all_surveys, missing = "fiml", std.lv = T)
semPaths(second.fit, whatLabels = "std", layout = "tree")
summary(second.fit, standardized = TRUE, rsquare=TRUE)
modindices(second.fit, sort. = TRUE, minimum.value = 3.84)
fitmeasures(second.fit)
corolations<-(second.fit)
fitted<-fitted(second.fit)

# Control for negative items

PWB_1, PWB_3, PWB_5, APSI_1, APSI_2,  APSI_4,  APSI_5,  APSI_6, APSI_7, APSI_8,  LET_3, LET_5, MLQ_1, MLQ_2, MLQ_3, MLQ_4, MLQ_5, MLQ_6,MLQ_7, MLQ_8, MLQ_10

bifactor.model = 'F1 =~ APSI_1 + APSI_2 +  APSI_4 +  APSI_5 + APSI_7 + APSI_8 + MLQ_4 + MLQ_6
                F2  =~ PWB_1 + PWB_3 + PWB_5 + APSI_6 + LET_3 + LET_5
              F3 =~ MLQ_2, MLQ_3 + MLQ_7 + MLQ_8 + MLQ_10
              PWB_1 ~~ PWB_3 + PWB_5 + APSI_6 + LET_3 + LET_5
              PWB_3 ~~ PWB_5 + APSI_6 + LET_3 + LET_5
              PWB_5 ~~ APSI_6 + LET_3 + LET_5
              APSI_6 ~~ LET_3 + LET_5
              LET_3 ~~ LET_5'
              
bifactor.fit=cfa(bifactor.model, data=all_surveys, missing = "fiml", std.lv = T)
semPaths(bifactor.fit, whatLabels = "std", layout = "tree")
summary(bifactor.fit, standardized = TRUE, rsquare=TRUE)
modindices(bifactor.fit, sort. = TRUE, minimum.value = 3.84)
fitmeasures(bifactor.fit)

 