---
title: "B5Fn_CFA"
author: "Levi Brackman"
date: "22 July 2015"
output: html_document
---

I see myself as someone who:

1.	Is sometimes rude to others. (Agreeableness)
2.	Has a forgiving nature.(Agreeableness)
3.	Is considerate and kind to almost everyone.(Agreeableness)
4.	Does a thorough job.(Conscientiousness)
5.	Tends to be lazy. (reverse-scored) (Conscientiousness)
6.	Does things efficiently.(Conscientiousness)
7.	Is talkative.(Extraversion)
8.	Is outgoing, sociable.(Extraversion)
9.	Is reserved. (reverse-scored) (Extraversion)
10.	Worries a lot. (Neuroticism)
11.	Gets nervous easily. (Neuroticism)
12.	Is relaxed, handles stress well. (reverse-scored) (Neuroticism)
13.	Is original, comes up with new ideas. (Openness to Experience)
14.	Values artistic, aesthetic experiences. (Openness to Experience)
15.	Has an active imagination, is original, comes up with new ideas. (Openness to Experience)

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
```
#loadthedata
```{r}
data <- read.csv("~/Psychometric_study_data/allsurveysYT1.csv")
B5<-select(data, B5F_1  , B5F_2 , B5F_3, B5F_4 ,  B5F_5 , B5F_6 ,B5F_7 , B5F_8 , B5F_9 , B5F_10 , B5F_11 , B5F_12 , B5F_13 , B5F_14 , B5F_15)
B5$B5F_12  <-  9- B5$B5F_12
B5$B5F_9  <-  9- B5$B5F_9
B5$B5F_5  <-  9- B5$B5F_5
B5<-tbl_df(B5)
B5
View(data)
```
#create plots
```{r}
#ggpairs(B5, columns = 1:15, title="Big 5 Marsh" )

```
#create the models
```{r}
five.model= ' agreeableness  =~ B5F_1 +  B5F_2  + B5F_3    
              conscientiousness =~  B5F_4 + B5F_5 + B5F_6          
              extraversion =~ B5F_7 + B5F_8 + B5F_9       
              neuroticism =~ B5F_10 + B5F_11 + B5F_12      
              openness  =~  B5F_13 +  B5F_14 + B5F_15' 

one.model= 'Big5 =~ B5F_1 +  B5F_2  + B5F_3 + B5F_4 + B5F_5 + B5F_6 + B5F_7 + B5F_8 + B5F_9 + B5F_10 + B5F_11 + B5F_12 + B5F_13 +  B5F_14 + B5F_15'
```
#run the models
```{r}
five.fit=cfa(five.model, data=B5, missing = "fiml")
one.fit=cfa(one.model, data=B5, missing = "fiml")
```

#create pictures
```{r}
semPaths(five.fit, whatLabels = "std", layout = "tree")
semPaths(one.fit, whatLabels = "std", layout = "tree")
```
#summaries
```{r}
summary(five.fit, standardized = TRUE, rsquare=TRUE)
summary(one.fit, standardized = TRUE, rsquare=TRUE)
```
#Residual correlations
```{r}
correl = residuals(five.fit, type="cor")
correl
View(correl$cor)
correl1 = residuals(one.fit, type="cor")
correl1
View(correl1$cor)
```
#zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels = residuals(five.fit, type = "standardized")
View(zcorrels$cov)
zcorrels1 = residuals(one.fit, type = "standardized")
View(zcorrels1$cov)
```
#Modification indicies
```{r}
modindices(five.fit, sort. = TRUE, minimum.value = 3.84)
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
```
#Fit Measures
```{r}
fitmeasures(five.fit)
fitmeasures(one.fit)
```
#Create dataset for Target rotation
```{r}
B5FTR<-select(data, B5F_1  , B5F_2 , B5F_3, B5F_4 ,  B5F_5 , B5F_6 ,B5F_7 , B5F_8 , B5F_9 , B5F_10 , B5F_11 , B5F_12 , B5F_13 , B5F_14 , B5F_15)
colnames(B5FTR) <- c("1","2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15")
#Target Roration
```{r}
Targ_key <- make.keys(15,list(f1=1:3,f2=4:6, f3=7:9, f4=10:12, f5=13:15))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
B5FTR_cor<-corFiml(B5FTR)
out_targetQ <- fa(B5FTR_cor,5,rotate="TargetQ", n.obs = 670, Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
