---
title: "CFA & Trarget Rotation PWB"
author: "Levi Brackman"
date: "26 Jan 2016"
output: html_document
---

1.	I live one day at a time and don't really think about the future. (rs)
2.	I tend to focus on the present, because the future always brings me problems. (rs)
3.	My daily activities often seem trivial and unimportant to me. (rs)
4.	I don't have a good sense of what it is that I am trying to accomplish in my life. (rs)
5.	I used to set goals for myself, but that now seems a waste of time. (rs)
6.	I enjoy making plans for the future and working to make them a reality. 
7.	I am an active person in carrying out the plans I set for myself. 
8.	Some people wander aimlessly through life, but I am not one of them. 
9.	I sometimes feel as if I've done all there is to do in life. (rs)

---

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
```
#loadthedata
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
data<-tbl_df(data)
PWB<-select(data, PWB_1, PWB_2, PWB_3, PWB_4, PWB_5, PWB_6,PWB_7, PWB_8, PWB_9)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
PWB<-tbl_df(PWB)
PWB

```
#create plots
```{r}
#ggpairs(PWB, columns = 1:15, title="Big 5 Marsh" )

```
#create the models
```{r}
two.model= ' Factor1  =~ PWB_1 +  PWB_3  + PWB_4 + PWB_5 + PWB_6 + PWB_9   
              Factor2 =~   PWB_2+ PWB_7 + PWB_8
'  #Models two factors:Positive and Negative     
              

one.model= 'PWB =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_6 + PWB_7 + PWB_8 + PWB_9' #Models as a single purpose factor
```
Second order models
```{r}

second.model = ' Purpose  =~ PWB_1 +  PWB_3  + PWB_4 + PWB_5 + PWB_6 + PWB_9  
              Positive =~   PWB_2+ PWB_7 + PWB_8
              PWB =~ NA*Purpose + Positive
            
' #Second order models as Purpose being the higher factor made up of Purpose and Positive

```
Bifactor (like model 7 in Marsh, Scalas & Nagengast, 2010)
```{r}

bifactor.negative.model = 'Negative =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_9  
                                     PWB =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_6 + PWB_7 + PWB_8 + PWB_9 
'#Models bifactor as the negatively worded item as a factor uncorolated with the main factor

bifactor.model1 = 'PWB =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_6 + PWB_7 + PWB_8 + PWB_9
                Negative  =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_9   
              Positive =~   PWB_6 + PWB_7 + PWB_8
                PWB ~~ 0*Negative
                PWB ~~ 0*Positive
                Negative~~0*Positive
#Add to model to constrain variable to stay positive
PWB_2 ~~ a*PWB_2
a > 0

'#Models bifactor with Positive and Purpose as factors uncorolated with the main factor

```
#run the models
```{r}
two.fit=cfa(two.model, data=PWB)
one.fit=cfa(one.model, data=PWB)
second.fit=cfa(second.model, data=PWB)
bifactor1.fit=cfa(bifactor.model1, data=PWB)
bifactor.negative.fit=cfa(bifactor.negative.model, data=PWB)
```

#create pictures
```{r}
semPaths(two.fit, whatLabels = "std", layout = "tree")
semPaths(one.fit, whatLabels = "std", layout = "tree")
semPaths(second.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor1.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor.negative.fit, whatLabels = "std", layout = "tree")
```
#summaries
```{r}
summary(two.fit, standardized = TRUE, rsquare=TRUE)
summary(one.fit, standardized = TRUE, rsquare=TRUE)
summary(second.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor1.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.negative.fit, standardized = TRUE, rsquare=TRUE)
```
#Residual correlations
```{r}
correl = residuals(two.fit, type="cor")
correl
View(correl$cor)
correl1 = residuals(one.fit, type="cor")
correl1
View(correl1$cor)
correl0 = residuals(second.fit, type="cor")
correl0
View(correl0$cor)
correl4 = residuals(bifactor1.fit, type="cor")
correl4
View(correl4$cor)
correl3 = residuals(bifactor.negative.fit, type="cor")
correl3
View(correl3$cor)
```
#zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels = residuals(two.fit, type = "standardized")
View(zcorrels$cov)
zcorrels1 = residuals(one.fit, type = "standardized")
View(zcorrels1$cov)
zcorrel0 = residuals(second.fit, type="cor")
zcorrel0
View(zcorrel0$cor)
zcorrel3 = residuals(bifactor.negative.fit, type="cor")
zcorrel3
View(zcorrel3$cor)
zcorrel4 = residuals(bifactor1.fit, type="cor")
zcorrel4
View(zcorrel4$cor)
```
#Modification indicies
```{r}
modindices(two.fit, sort. = TRUE, minimum.value = 3.84)
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
modindices(bifactor1.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.negative.fit, sort. = TRUE, minimum.value = 3.84)
```
#Fit Measures
```{r}
fitmeasures(two.fit)#Models two factors:Positive and Negative for Purpose  
fitmeasures(one.fit) #Models as a single purpose factor
fitmeasures(second.fit)#Second order models as Purpose being the higher factor made up of Purpose and Positive
fitmeasures(bifactor1.fit)#Models bifactor with Positive and Purpose as factors uncorolated with the main factor
fitmeasures(bifactor.negative.fit)#Models bifactor as the negatively worded item as a factor uncorolated with the main factor
```
#Create dataset for Target rotation
```{r}
all_surveys<-read.csv("allsurveys.csv")
PWB<-select(all_surveys, PWB_1, PWB_4,PWB_5,PWB_6,PWB_9,PWB_2,PWB_3,PWB_7,PWB_8,PWB_10)
PWB<- data.frame(apply(PWB,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

PWB<-tbl_df(PWB)
PWB$PWB_9  <-  8- PWB$PWB_9
PWB
str(PWB)
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8", "9", "10")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(10,list(f1=1:5,f2=6:10))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(PWB,2,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
---
Droping PWB_9 which is a reversed scoded question

#Create dataset for Target rotation
```{r}
all_surveys<-read.csv("allsurveysYT1_Jan2016.csv")
PWB<-select(all_surveys, PWB_1, PWB_3,PWB_4, PWB_5,PWB_6,PWB_9, PWB_8,PWB_7)
PWB<- data.frame(apply(PWB,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

PWB<-tbl_df(PWB)
PWB
str(PWB)
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(8,list(f1=1:6,f2=7:8))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(PWB,2,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))

