---
title: "GRIT CFA & TR Youth"
author: "Levi Brackman"
date: "28 July 2015"
output: html_document
---
```{r}
```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
```
#loadthedata
```{r}
all_surveys<-read.csv("allsurveysYT1.csv")
all_surveys<-tbl_df(all_surveys)
all_surveys
GRIT<-select(all_surveys, GRIT_4, GRIT_5, GRIT_6, GRIT_7, GRIT_8, GRIT_9, GRIT_10, GRIT_11)
GRIT<- data.frame(apply(GRIT,2, as.numeric))
GRIT<-tbl_df(GRIT)
GRIT
```
#Create the Models#
As only one factor
```{r}
one.factor = 'GRIT =~ GRIT_4 + GRIT_5 + GRIT_6 + GRIT_7 + GRIT_8 + GRIT_9 + GRIT_10 + GRIT_11
' 
```
Two Factor, Positive and Nagative Model
```{r}
first.model= ' Consistency =~ GRIT_4 + GRIT_5 + GRIT_6 + GRIT_7  
             Preserverence =~   GRIT_8 + GRIT_9 + GRIT_10 + GRIT_11
' 
```

Bifactor Models (similar to Models 6, 7 & 8 in Marsh, Scalas & Nagengast, 2010)
```{r}

bifactor.model = 'GRIT =~ GRIT_4 + GRIT_5 + GRIT_6 + GRIT_7 + GRIT_8 + GRIT_9 + GRIT_10 + GRIT_11
                Consistency =~ GRIT_4 + GRIT_5 + GRIT_6 + GRIT_7  
             Preserverence =~   GRIT_8 + GRIT_9 + GRIT_10 + GRIT_11
                GRIT ~~ 0*Consistency
                GRIT ~~ 0*Preserverence
                Consistency~~0*Preserverence
'
```
Running the models
```{r}
one.fit=cfa(one.factor, data=GRIT, missing = "fiml", std.lv = T)
two.fit=cfa(first.model, data=GRIT, missing = "fiml", std.lv = T)
bifactor.fit=cfa(bifactor.model, data=GRIT, missing = "fiml", orthogonal = TRUE, std.lv = T)

```
Create pictures of models
```{r}
#One Factor
semPaths(one.fit, whatLabels = "std", layout = "tree", title=T)
#Two Factors Positive and Nagative
semPaths(two.fit, whatLabels = "std", layout = "tree")
#Bifactor Models (similar to Models 6, 7 & 8 in Marsh, Scalas & Nagengast, 2010)
semPaths(bifactor.fit, whatLabels = "std", layout = "tree")

```
Summaries
```{r}
summary(one.fit, standardized = TRUE, rsquare=TRUE)
summary(two.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.fit, standardized = TRUE, rsquare=TRUE)
```
Residual correlations
```{r}
correl.1 = residuals(one.fit, type="cor")
correl.1
#View(correl.1$cor)
correl = residuals(two.fit, type="cor")
correl
correl3 = residuals(bifactor.fit, type="cor")
correl3
```
zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels10 = residuals(one.fit, type = "standardized")
zcorrels10$cov
zcorrels = residuals(two.fit, type = "standardized")
zcorrels$cov
zcorrels5 = residuals(bifactor.fit, type = "standardized")
zcorrels5$cov
```
Modification indicies
```{r}
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
modindices(two.fit, sort. = TRUE, minimum.value = 3.84)
modindices(bifactor.fit, sort. = TRUE, minimum.value = 3.84)

```
Fit Measures
```{r}
fitmeasures(one.fit)
fitmeasures(two.fit)
fitmeasures(bifactor.fit)
```
```
Two factors Consitency and preseverence

```{r}
all_surveys<-read.csv("allsurveysYT1.csv")
all_surveys<-tbl_df(all_surveys)
all_surveys
GRIT<-select(all_surveys, GRIT_4, GRIT_5, GRIT_6, GRIT_7, GRIT_8, GRIT_9, GRIT_10, GRIT_11)
GRIT<- data.frame(apply(GRIT,2, as.numeric))
GRIT<-tbl_df(GRIT)
GRIT
```

Target Rotation

```{r, echo=FALSE}
colnames(GRIT) <- c("1","2", "3", "4", "5", "6", "7", "8")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be GRIT
Targ_key <- make.keys(8,list(f1=1:4,f2=5:8))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(GRIT,2,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```


