---
title: "LS CFA TR Youth"
author: "Levi Brackman"
date: "28 July 2015"
output: html_document
---
1.	In most ways my life is close to my ideal. 
2.	The conditions of my life are excellent. 
3.	I am satisfied with my life. 
4.	So far I have gotten the important things I want in life. 
5.	If I could live my life over, I would change almost nothing. 
---

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
```
#loadthedata
```{r}
data <- read.csv("~/Psychometric_study_data/allsurveysYT1.csv")
data<-tbl_df(data)
LS<-select(data, LS_1,	LS_2,	LS_3,	LS_4,	LS_5)

LS<-tbl_df(LS)
LS
```

#Create the Models#
As only one factor
```{r}
one.factor = 'LS =~ LS_1 +  LS_2  + LS_3  + LS_4 + LS_5  
' 
```
Two Factor - diffecult to justify from the theoretical standpoint but will try to see the fit anyway
```{r}
first.model= ' F1 =~ LS_1 +  LS_2     
             F2 =~   LS_3 + LS_4 + LS_5  
' 

```
Running the models
```{r}
one.fit=cfa(one.factor, data=LS, missing = "fiml", std.lv = T)
two.fit=cfa(first.model, data=LS, missing = "fiml", std.lv = T)
```
Create pictures of models
```{r}
#One Factor
semPaths(one.fit, whatLabels = "std", layout = "tree", title=T)
#Two Factors 
semPaths(two.fit, whatLabels = "std", layout = "tree")

```
Summaries
```{r}
summary(one.fit, standardized = TRUE, rsquare=TRUE)
summary(two.fit, standardized = TRUE, rsquare=TRUE)

```
Residual correlations
```{r}
correl.1 = residuals(one.fit, type="cor")
correl.1
#View(correl.1$cor)
correl = residuals(two.fit, type="cor")
correl
#View(correl$cor)

```
zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels10 = residuals(one.fit, type = "standardized")
zcorrels10$cov
zcorrels = residuals(two.fit, type = "standardized")
zcorrels$cov

```
Modification indicies
```{r}
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
modindices(two.fit, sort. = TRUE, minimum.value = 3.84)

```
Fit Measures
```{r}
fitmeasures(one.fit)
fitmeasures(two.fit)
```
#Create dataset for Target rotation
```{r}
LSTR<-select(data, LS_1,	LS_2,	LS_3,	LS_4,	LS_5)

colnames( LSTR) <- c("1","2", "3", "4", "5")
 LSTR<-tbl_df( LSTR)
 LSTR
#Target Roration
```{r}
Targ_key <- make.keys(5,list(f1=1:5))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
LSTR_cor <- corFiml(LSTR) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(LSTR_cor,1,rotate="TargetQ", n.obs = 772, Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```