---
title: "EFA CFA TR APSI YOUTH"
author: "Levi Brackman"
date: "26 January 2016"
output: html_document
---
1.	I have a definite sense of purpose in life.
2.	I have a firm sense of who I am.
3.	I have a set of basic beliefs and values that guide my actions and decisions.
4.	I know what I want out of life.
5.	I have a clear set of personal values or moral standards.
6.	I don't know where I fit in the world.
7.	I have specific personal goals for the future.
8.	I have a clear sense of who I want to be when I am an adult.

```{r}

##load packages
library(psych)
library(GPArotation)
library(plyr)
library(dplyr)
library(lavaan)
library(semPlot)
# data preparation
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
APSI<-select(data,  APSI_1,  APSI_2,  APSI_3,  APSI_4,  APSI_5,  APSI_6, APSI_7,  APSI_8)
APSI$APSI_6  <-  6- APSI$APSI_6
APSI<- data.frame(apply(APSI,2, as.numeric))
str(APSI)
colnames(APSI) <- c("1","2", "3", "4", "5", "6", "7", "8")
 APSI<- APSI[complete.cases(APSI[,]),]

```
##EFA
##number of factors
##parallal analysis and scree plot
```{r}
parallel<-fa.parallel(APSI, fm="ml",fa="fa")
#one factors are greater than one Eigenvalue scree plot says there are two factors. Paralel analysis suggests 4 factors
#eigenvalues (kaiser)
parallel$fa.values
#over 1=1, over .7=0
```
#doing aprincipal components analysis to see how many factors there might be using that method
#Deal with NA doing principle componant analysis
```{r}
princomp(na.omit(APSI), cor = TRUE)
parallel2<-princomp(na.omit(APSI), cor = TRUE)
summary(parallel2)
plot(parallel2)##results show at least two factors
```
#simple structure
```{r}
twofactor<-fa(APSI, nfactors=2, rotate="oblimin", fm="ml")
twofactor#not a good fit
1-((twofactor$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))

threefactor<-fa(APSI, nfactors=3, rotate="oblimin", fm="ml")
threefactor#Still not a great fit. 1, 2, 4, 7, 8 are one factor 3 and 5 seem to be thir own factors and 6 crossloads on all factors. 
1-((threefactor$STATISTIC - threefactor$dof)/(threefactor$null.chisq- threefactor$null.dof))

fourfactor<-fa(APSI, nfactors=4, rotate="oblimin", fm="ml")
fourfactor#An over fit
1-((fourfactor$STATISTIC - fourfactor$dof)/(fourfactor$null.chisq- fourfactor$null.dof))

fa2latex(fa(APSI,2, rotate="oblimin", fm="ml"),heading="Table 2. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation 
of APSI")
fa2latex(fa(APSI,3, rotate="oblimin", fm="ml"),heading="Table 3. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation 
of APSI")
fa2latex(fa(APSI,4, rotate="oblimin", fm="ml"),heading="Table 4. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation 
of APSI")

```
#question 1,4,7,8 seem to talk about purpose. so try as one factr
```{r}
 APSI12478<-select(APSI, 1, 2, 4,7,8)
 APSI12478<-tbl_df(APSI12478)
  APSI12478
twofactorAPSI12478<-fa(APSI12478, nfactors=1, rotate="varimax", fm="ml")
twofactorAPSI12478#The TLI is good but the RMSEA is a poor fit
fa2latex(fa(APSI12478,1, rotate="oblimin", fm="ml"),heading="Table 5. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation
of APSI")
#CFI
1-((twofactorAPSI12478$STATISTIC - twofactorAPSI12478$dof)/(twofactorAPSI12478$null.chisq- twofactorAPSI12478$null.dof))

```
#question 1,4,7,8 seem to talk about purpose. so try as one factr
```{r}
 APSI124578<-select(APSI, 1, 2, 4,5, 7,8)
APSI124578<-tbl_df(APSI124578)
APSI124578
twofactorAPSI124578<-fa(APSI124578, nfactors=1, rotate="varimax", fm="ml")
twofactorAPSI124578#The TLI is good but the RMSEA is a poor fit
fa2latex(fa(APSI124578,1, rotate="oblimin", fm="ml"),heading="Table 5. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation
of APSI")
#CFI
1-((twofactorAPSI124578$STATISTIC - twofactorAPSI124578$dof)/(twofactorAPSI124578$null.chisq- twofactorAPSI124578$null.dof))

```
#drop question 2 and only uuse question 1,4,7,8 seem to talk about purpose. so try as one factr
```{r}
 APSI1478<-select(APSI, 1, 4,7,8)
 APSI1478<-tbl_df(APSI1478)
  APSI1478
twofactorAPSI1478<-fa(APSI1478, nfactors=1, rotate="varimax", fm="ml")
fa2latex(fa(APSI1478,1, rotate="oblimin", fm="ml"),heading="Table 6. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation
of APSI")
twofactorAPSI1478#clearly shows that this is all one factor. Droping 2 makes it a much better fit.
#CFI
1-((twofactorAPSI1478$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))
```
#question 6 is negative but talks about fit in the world, question 2 talks about know "who I am" see if fits into one factor
```{r}
 APSI26<-select(APSI, 3, 5,6)
 APSI26<-tbl_df(APSI26)
 APSI26
twofactorAPSI26<-fa(APSI26, nfactors=3, rotate="varimax", fm="ml")
fa2latex(fa(APSI26,3, rotate="oblimin", fm="ml"),heading="Table 7. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation
of APSI")
twofactorAPSI26#seems to be a good fit
#CFI
1-((twofactorAPSI26$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))
```
#question three and five talk about morals and values and could be one factor
```{r}
 APSI35<-select(APSI, 3,5)
 APSI35<-tbl_df(APSI35)
 APSI35
twofactorAPSI35<-fa(APSI35, nfactors=1, rotate="varimax", fm="ml")
fa2latex(fa(APSI35,1, rotate="oblimin", fm="ml"),heading="Table 8. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation
of APSI")
twofactorAPSI35#seems to load well on one factor
#CFI
1-((twofactorAPSI35$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))

#What are the factors
#Factor 1 (questions 1, 4, 7, 8) is purpose
#Factor 2 (questions 3,5) is moral values
#Factor 3 (questions 2,6) fit in the world, knowledge of who I am
```
#Finding Alpha
```{r}
alpha(APSI, na.rm = TRUE, check.keys=TRUE)
```
#Create dataset for Target rotation
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
 APSI<-select(data,  APSI_1, APSI_2, APSI_4, APSI_7,  APSI_8,    APSI_5, APSI_3,  APSI_6)
APSI$APSI_6  <-  6- APSI$APSI_6
APSI<- data.frame(apply(APSI,2, as.numeric))

```
Load packedges
```{r}
library(GPArotation)
library(psych)
library(dplyr)

colnames(APSI) <- c("1","2", "3", "4", "5", "6", "7", "8")
```
Trying to see whether we can make this into two factors
```{r}
Targ_key <- make.keys(8,list(f1=1:5,f2=6:8))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
APSI_cor <- corFiml(APSI)
APSI_cor
out_targetQ <- fa(APSI_cor,2,rotate="TargetQ",n.obs = 807,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
fa2latex(fa(APSI_cor,2,rotate="TargetQ",n.obs = 807,Target=Targ_key), heading="Table 9. Factor Loadings for Confirmatory Factor Analysis with Target Rotation of APSI")
out_targetQ#get a heywood case. really poor fit
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))

```
#Create dataset for Target rotation
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
APSI<-select(data,  APSI_1, APSI_2, APSI_4, APSI_7,  APSI_8,    APSI_5, APSI_3,  APSI_6)
APSI$APSI_6  <-  6- APSI$APSI_6
APSI<- data.frame(apply(APSI,2, as.numeric))
colnames(APSI) <- c("1","2", "3", "4", "5", "6", "7","8")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be MLQ
Targ_key <- make.keys(8,list(f1=1:6,f2=7:8))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
APSI_cor <- corFiml(APSI)
APSI_cor
out_targetQ <- fa(APSI_cor,2,rotate="TargetQ",n.obs = 807,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]#many cross loadings
fa2latex(fa(APSI_cor,2,rotate="TargetQ",n.obs = 807,Target=Targ_key), heading="Table 10. Factor Loadings for Confirmatory Factor Analysis with Target Rotation of APSI")
out_targetQ#still not a great fit
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))

```
#Create dataset for Target rotation droping question 3 that talks about having belifes and values and loads on all factors
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
APSI<-select(data,  APSI_1, APSI_2, APSI_4, APSI_7,  APSI_8,  APSI_5, APSI_3,  APSI_6)
APSI$APSI_6  <-  6- APSI$APSI_6
APSI<- data.frame(apply(APSI,2, as.numeric))
colnames(APSI) <- c("1","2", "3", "4", "5", "6", "7", "8")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
Targ_key <- make.keys(8,list(f1=1:6,f2=7, f3=8))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
APSI_cor <- corFiml(APSI)
out_targetQ <- fa(APSI_cor,3,rotate="TargetQ",n.obs = 807,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
fa2latex(fa(APSI_cor,3,rotate="TargetQ",n.obs = 807,Target=Targ_key), heading="Table 11. Factor Loadings for Confirmatory Factor Analysis with Target Rotation of APSI")
out_targetQ#its a good fit but the second factor does not load at all. 1, 4, 7, 8 work well as one factor 3, 5 and 6 are problematic. 
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
#Create dataset for Target rotation as one factor
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
APSI<-select(data,  APSI_1, APSI_2, APSI_3, APSI_4, APSI_5, APSI_6, APSI_7, APSI_8)
APSI$APSI_6  <-  6- APSI$APSI_6
APSI<- data.frame(apply(APSI,2, as.numeric))
colnames(APSI) <- c("1","2", "3", "4", "5", "6", "7", "8")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
Targ_key <- make.keys(8,list(f1=1:8))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
APSI_cor <- corFiml(APSI)
out_targetQ <- fa(APSI_cor,1,rotate="TargetQ",n.obs = 807,Target=Targ_key) #TargetT for orthogonal rotation
fa2latex(fa(APSI_cor,1,rotate="TargetQ",n.obs = 807,Target=Targ_key), heading="Table 1. Factor Loadings for Confirmatory Factor Analysis with Target Rotation of APSI")
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ#its a good fit but the second factor does not load at all. 1, 4, 7, 8 work well as one factor 3, 5 and 6 are problematic. 
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
Lavaan for one factor model
```{r}
```
#create the models
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
APSI<-select(data,  APSI_1, APSI_2, APSI_3, APSI_4, APSI_5, APSI_6, APSI_7, APSI_8)
one.model= ' Factor1  =~ APSI_1 + APSI_2 + APSI_3 + APSI_4 + APSI_5 + APSI_6 + APSI_7 + APSI_8'
one.fit=cfa(one.model, data=APSI, missing = "fiml")
semPaths(one.fit, whatLabels = "std", layout = "tree")
summary(one.fit, standardized = TRUE, rsquare=TRUE)
correl1 = residuals(one.fit, type="cor")
correl1
View(correl1$cor)
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
fitmeasures(one.fit) #Models as a single purpose factor

data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
APSI<-select(data,  APSI_1, APSI_2, APSI_3, APSI_4, APSI_5, APSI_6, APSI_7, APSI_8)
one.model= ' Factor1  =~ APSI_1 + APSI_2 + APSI_4 + APSI_5 + APSI_7 + APSI_8
Factor 2 =~ APSI_3  
Factor 3 =~ APSI_6'
one.fit=cfa(one.model, data=APSI, missing = "fiml")
semPaths(one.fit, whatLabels = "std", layout = "tree")
summary(one.fit, standardized = TRUE, rsquare=TRUE)
correl1 = residuals(one.fit, type="cor")
correl1
View(correl1$cor)
correl2 = residuals(one.fit, type="standardized")
correl2$cov
View(correl2$cov)
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
summary(one.fit)
fitmeasures(one.fit) #Models as a single purpose factor
inspect(one.fit,what="std")
fitted(one.fit)
cov2cor(inspect(one.fit, "coefficients")$psi) 
 #Models two factors:Positive and Negative  
```
Misc code for exportign tabel
```{r}
#fa.results(out_targetQ)
#xtable(out_targetQ)

#source("http://bioconductor.org/biocLite.R")
#biocLite(c("graph", "RBGL", "Rgraphviz"))
#library(Rgraphviz)
#library(schoRsch)
#library(xtable)
#library(knitr)
#library(devtools)

#fa2latex(fa(APSI,1,rotate="oblimin", fm="ml"),heading="Table 1. Factor analysis OF APSI as One Factor")


