---
title: "Life Satisfaction CFA & Traget Rotation"
author: "Levi Brackman"
date: "23 July 2015"
output: html_document
---
1.	In most ways my life is close to my ideal. 
2.	The conditions of my life are excellent. 
3.	I am satisfied with my life. 
4.	So far I have gotten the important things I want in life. 
5.	If I could live my life over, I would change almost nothing. 
---

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
```
#loadthedata
```{r}
data <- read.csv("~/Psychometric_study_data/allsurveysT1.csv")
data<-tbl_df(data)
LET<-select(data, LET_1,	LET_2,	LET_3,	LET_4,	LET_5,	LET_6)
LET$LET_1  <-  6- LET$LET_1
LET$LET_3  <-  6- LET$LET_3
LET$LET_5  <-  6- LET$LET_5

LET<-tbl_df(LET)
LET

```
#create plots
```{r}
#ggpairs(LET, columns = 1:15, title="Big 5 Marsh" )

```
#create the models
```{r}
two.model= ' Negative =~ LET_1 +  LET_3  + LET_5   
             Positive =~   LET_2 + LET_4 + LET_6'       

one.model= 'LET =~ LET_1 +  LET_2  + LET_3 + LET_4 + LET_5 + LET_6'
```
#run the models
```{r}
two.fit=cfa(two.model, data=LET)
one.fit=cfa(one.model, data=LET)
```

#create pictures
```{r}
semPaths(two.fit, whatLabels = "std", layout = "tree")
semPaths(one.fit, whatLabels = "std", layout = "tree")
```
#summaries
```{r}
summary(two.fit, standardized = TRUE, rsquare=TRUE)
summary(one.fit, standardized = TRUE, rsquare=TRUE)
```
#Residual correlations
```{r}
correl = residuals(two.fit, type="cor")
correl
View(correl$cor)
correl1 = residuals(one.fit, type="cor")
correl1
View(correl1$cor)
```
#zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels = residuals(two.fit, type = "standardized")
View(zcorrels$cov)
zcorrels1 = residuals(one.fit, type = "standardized")
View(zcorrels1$cov)
```
#Modification indicies
```{r}
modindices(two.fit, sort. = TRUE, minimum.value = 3.84)
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
```
#Fit Measures
```{r}
fitmeasures(two.fit)
fitmeasures(one.fit)
```
#Create dataset for Target rotation
```{r}
LETTR<-select(LET, LET_1  , LET_2 , LET_3, LET_4 ,  LET_5 , LET_6)
colnames(LETTR) <- c("1","2", "3", "4", "5", "6")
#Target Roration
```{r}
Targ_key <- make.keys(6,list(f1=1:6))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(LETTR,1,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
As two Factor
```{r}
LETTR2<-select(LET, LET_1  , LET_3 , LET_5, LET_2 ,  LET_4 , LET_6)
colnames(LETTR2) <- c("1","2", "3", "4", "5", "6")
Targ_key <- make.keys(6,list(f1=1:3, f2=4:6))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(LETTR2,2,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ

```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
