---
title: "LET CFA Account for Pos and Neg Models"
author: "Levi Brackman"
date: "25 July 2015"
output: html_document
---
---
1.	In most ways my life is close to my ideal. 
2.	The conditions of my life are excellent. 
3.	I am satisfied with my life. 
4.	So far I have gotten the important things I want in life. 
5.	If I could live my life over, I would change almost nothing. 
---

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
```
#loadthedata
```{r}
data <- read.csv("~/Psychometric_study_data/allsurveysT1.csv")
data<-tbl_df(data)
LET<-select(data, LET_1,	LET_2,	LET_3,	LET_4,	LET_5,	LET_6)
LET$LET_1  <-  6- LET$LET_1
LET$LET_3  <-  6- LET$LET_3
LET$LET_5  <-  6- LET$LET_5

LET<-tbl_df(LET)
LET
```

#Create the Models#
As only one factor
```{r}
one.factor = 'LET =~ LET_1 +  LET_2  + LET_3  + LET_4 + LET_5 + LET_6
' 
```
Two Factor, Positive and Nagative Model
```{r}
first.model= ' Negative =~ LET_1 +  LET_3  + LET_5   
             Positive =~   LET_2 + LET_4 + LET_6
' 
```
Second order models
```{r}

second.model = ' Negative =~ LET_1 +  LET_3  + LET_5   
              Positive =~   LET_2 + LET_4 + LET_6
              LET =~ NA*Positive + Negative
'

alternative.model  = 'Negative =~ LET_1 +  LET_3  + LET_5   
              Positive =~ LET_2 + LET_4 + LET_6
              LET =~ NA*Positive + Negative
              LET~~1*LET
'

```
Bifactor Models (similar to Models 6, 7 & 8 in Marsh, Scalas & Nagengast, 2010)
```{r}

bifactor.model = 'Negative =~ LET_1 +  LET_3  + LET_5   
              Positive =~   LET_2 + LET_4 + LET_6
              Life Satisfaction =~ LET_1 +  LET_2  + LET_3 + LET_4 + LET_5 + LET_6
'
```
Bifactor only with Negative questions protioned out (like model 7 in Marsh, Scalas & Nagengast, 2010)
```{r}

bifactor.negative.model = 'Negative =~ LET_1 +  LET_3  + LET_5   
                        LET =~ LET_1 +  LET_2  + LET_3 + LET_4 + LET_5 + LET_6
'
```
Bifactor only with Positive questions protioned out (like model 8 in Marsh, Scalas & Nagengast, 2010)
```{r}
bifactor.positive.model = 'Positive =~   LET_2 + LET_4 + LET_6
                        LET =~ LET_1 +  LET_2  + LET_3 + LET_4 + LET_5 + LET_6
'
```
Alternative method of writing bifactor model
```{r}
bifactor.model1 = 'LET =~ LET_1 +  LET_2  + LET_3 + LET_4 + LET_5 + LET_6
                Negative =~ LET_1 +  LET_3  + LET_5   
                Positive =~   LET_2 + LET_4 + LET_6
                LET ~~ 0*Negative
                LET ~~ 0*Positive
                Negative~~0*Positive
'
```
Running the models
```{r}
one.fit=cfa(one.factor, data=LET, std.lv = T)
two.fit=cfa(first.model, data=LET, std.lv = T)
second.fit=cfa(second.model, data=LET, std.lv = T)
alt.fit=cfa(alternative.model, data=LET, std.lv = T)
bifactor.fit=cfa(bifactor.model, data=LET, orthogonal = TRUE, std.lv = T)
bifactor.fit1=cfa(bifactor.model1, data=LET, orthogonal = TRUE, std.lv = T)
bifactor.negative.fit=cfa(bifactor.negative.model, data=LET, orthogonal = TRUE, std.lv = T)
bifactor.positive.fit=cfa(bifactor.positive.model, data=LET, orthogonal = TRUE, std.lv = T)

```
Create pictures of models
```{r}
#One Factor
semPaths(one.fit, whatLabels = "std", layout = "tree", title=T)
#Two Factors Positive and Nagative
semPaths(two.fit, whatLabels = "std", layout = "tree")
#Second order factors
semPaths(second.fit, whatLabels = "std", layout = "tree")
semPaths(alt.fit, whatLabels = "std", layout = "tree")
#Bifactor Models (similar to Models 6, 7 & 8 in Marsh, Scalas & Nagengast, 2010)
semPaths(bifactor.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor.fit1, whatLabels = "std", layout = "tree")
#Bifactor only with Negative questions protioned out (like model 7 in Marsh, Scalas & Nagengast, 2010)
semPaths(bifactor.negative.fit, whatLabels = "std", layout = "tree")
#Bifactor only with Negative questions protioned out (like model 7 in Marsh, Scalas & Nagengast, 2010)
semPaths(bifactor.positive.fit, whatLabels = "std", layout = "tree")
```
Summaries
```{r}
summary(one.fit, standardized = TRUE, rsquare=TRUE)
summary(two.fit, standardized = TRUE, rsquare=TRUE)
summary(second.fit, standardized = TRUE, rsquare=TRUE)
summary(alt.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.fit1, standardized = TRUE, rsquare=TRUE)
summary(bifactor.negative.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.positive.fit, standardized = TRUE, rsquare=TRUE)
```
Residual correlations
```{r}
correl.1 = residuals(one.fit, type="cor")
correl.1
#View(correl.1$cor)
correl = residuals(two.fit, type="cor")
correl
#View(correl$cor)
correl1 = residuals(second.fit, type="cor")
correl1
#View(correl1$cor)
correl2 = residuals(alt.fit, type="cor")
correl2
#View(correl2$cor)
correl3 = residuals(bifactor.fit, type="cor")
correl3
#View(correl3$cor)
correl4 = residuals(bifactor.fit1, type="cor")
correl4
#View(correl4$cor)
correl5 = residuals(bifactor.negative.fit, type="cor")
correl5
#View(correl5$cor)
correl6 = residuals(bifactor.positive.fit, type="cor")
correl6
#View(correl6$cor)
```
zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels10 = residuals(one.fit, type = "standardized")
zcorrels10$cov
zcorrels = residuals(two.fit, type = "standardized")
zcorrels$cov
#zcorrels1 = residuals(second.fit, type = "standardized")
#zcorrels1$cov
#zcorrels2 = residuals(alt.fit, type = "standardized")
#zcorrels2$cov
#zcorrels3 = residuals(bifactor.fit, type = "standardized")
#zcorrels3$cov
#zcorrels4 = residuals(bifactor1.fit, type = "standardized")
#zcorrels4$cov
zcorrels5 = residuals(bifactor.negative.fit, type = "standardized")
zcorrels5$cov
zcorrels6 = residuals(bifactor.positive.fit, type = "standardized")
zcorrels6$cov
```
Modification indicies
```{r}
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
modindices(two.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(second.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(alt.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.fit1, sort. = TRUE, minimum.value = 3.84)
modindices(bifactor.negative.fit, sort. = TRUE, minimum.value = 3.84)
modindices(bifactor.positive.fit, sort. = TRUE, minimum.value = 3.84)
```
Fit Measures
```{r}
fitmeasures(one.fit)
fitmeasures(two.fit)
fitmeasures(second.fit)
fitmeasures(alt.fit)
fitmeasures(bifactor.fit)
fitmeasures(bifactor.fit1)
fitmeasures(bifactor.negative.fit)
fitmeasures(bifactor.positive.fit)
```


