---
title: "LET Youth CFA"
author: "Levi Brackman"
date: "May 2 2016"
output: html_document
---
1.There is not enough purpose in my life. 
2. To me, the things I do are all worthwhile. 
3. Most of what I do seems trivial and unimportant to me. 
4. I value my activities a lot. 
5. I don't care very much about the things I do. 2
6. I have lots of reasons for living. 

---

```{r}
library(lubripack)
lubripack("knitr", "dplyr", "lavaan", "GPArotation", "psych", "car", "GGally", "semPlot", "ggplot2")
```
#loadthedata
```{r}
data <- read.csv("/Users/levibrackman/Documents/stats_march_2016/allsurveysYT1_Jan2016.csv")
LET<-select(data, LET_1,	LET_2,	LET_3,	LET_4,	LET_5,	LET_6)
LET$LET_1  <-  6- LET$LET_1
LET$LET_3  <-  6- LET$LET_3
LET$LET_5  <-  6- LET$LET_5

```
EFA Let
```{r}
LET=na.omit(LET)#removes missing data
#LET<- LET[complete.cases(LET[,]),]
```
##EFA
##number of factors
##parallal analysis and scree plot
```{r}
parallel<-fa.parallel(LET, fm="ml",fa="fa")
```
#three factors are greater than one Eigenvalue scree plot says there are three factors. 
#Paralel analysis suggests 6 factors
#eigenvalues (kaiser)
```{r}
parallel$fa.values
#over 1=1, over .7=2
```
#doign aprincipal components analysis to see how many factors there might be using that method
#Deal with NA doing principle componant analysis
```{r}
princomp(na.omit(LET), cor = TRUE)
parallel2<-princomp(na.omit(LET), cor = TRUE)
summary(parallel2)
plot(parallel2)##results show at least two factors
```
#simple structure
```{r}
onefactor<-fa(LET, nfactors=1, rotate="oblimin", fm="ml")
onefactor
twofactor<-fa(LET, nfactors=2, rotate="oblimin", fm="ml")
twofactor
```
LET_6 "I have lots of reasons for living." loads on both factors so droping it
```{r}
twofactorWO6<-fa(LET[,-6], nfactors=2, rotate="oblimin", fm="ml")
twofactorWO6
```
#Finding Alpha
```{r}
#alpha(LET, na.rm = TRUE, check.keys=TRUE)

```
#Create the Models, As only one factor
```{r}
one.factor = 'LET =~ LET_1 +  LET_2  +LET_3  + LET_4 + LET_5 + LET_6
' 
```
Two Factor, Positive and Nagative Model
```{r}
first.model= ' Negative =~ LET_1 +  LET_3  + LET_5   
             Positive =~   LET_2 + LET_4 + LET_6
' 
```
Second order models
```{r}

second.model = ' Negative =~ LET_1 +  LET_3  + LET_5   
              Positive =~   LET_2 + LET_4 + LET_6
              LET =~ NA*Positive + Negative
'

alternative.model  = 'Negative =~ LET_1 +  LET_3  + LET_5   
              Positive =~ LET_2 + LET_4 + LET_6
              LET =~ NA*Positive + Negative
              LET~~1*LET
'

```
Bifactor Models (similar to Models 6, 7 & 8 in Marsh, Scalas & Nagengast, 2010)
```{r}

bifactor.model = 'Negative =~ LET_1 +  LET_3  + LET_5   
              Positive =~   LET_2 + LET_4 + LET_6
              Life Satisfaction =~ LET_1 +  LET_2  + LET_3 + LET_4 + LET_5 + LET_6
'
```
Bifactor only with Negative questions protioned out (like model 7 in Marsh, Scalas & Nagengast, 2010)
```{r}

bifactor.negative.model = 'Negative =~ LET_1 +  LET_3  + LET_5   
                        LET =~ LET_1 +  LET_2  + LET_3 + LET_4 + LET_5 + LET_6
'
```
Bifactor only with Positive questions protioned out (like model 8 in Marsh, Scalas & Nagengast, 2010)
```{r}
bifactor.positive.model = 'Positive =~   LET_2 + LET_4 + LET_6
                        LET =~ LET_1 +  LET_2  + LET_3 + LET_4 + LET_5 + LET_6
'
```
Alternative method of writing bifactor model
```{r}
bifactor.model1 = 'LET =~ LET_1 +  LET_2  + LET_3 + LET_4 + LET_5 + LET_6
                Negative =~ LET_1 +  LET_3  + LET_5   
                Positive =~   LET_2 + LET_4 + LET_6
                LET ~~ 0*Negative
                LET ~~ 0*Positive
                Negative~~0*Positive
'
```
Running the models
```{r}
one.fit=cfa(one.factor, data=LET, missing = "fiml", std.lv = T)
two.fit=cfa(first.model, data=LET, missing = "fiml", std.lv = T)
second.fit=cfa(second.model, data=LET, missing = "fiml", std.lv = T)
alt.fit=cfa(alternative.model, data=LET, missing = "fiml", std.lv = T)
bifactor.fit=cfa(bifactor.model, data=LET, missing = "fiml", orthogonal = TRUE, std.lv = T)
bifactor.fit1=cfa(bifactor.model1, data=LET, missing = "fiml", orthogonal = TRUE, std.lv = T)
bifactor.negative.fit=cfa(bifactor.negative.model, missing = "fiml", data=LET, orthogonal = TRUE, std.lv = T)
bifactor.positive.fit=cfa(bifactor.positive.model, missing = "fiml", data=LET, orthogonal = TRUE, std.lv = T)

```
Create pictures of models
```{r}
#One Factor
semPaths(one.fit, whatLabels = "std", layout = "tree", title=T)
#Two Factors Positive and Nagative
semPaths(two.fit, whatLabels = "std", layout = "tree")
#Second order factors
semPaths(second.fit, whatLabels = "std", layout = "tree")
semPaths(alt.fit, whatLabels = "std", layout = "tree")
#Bifactor Models (similar to Models 6, 7 & 8 in Marsh, Scalas & Nagengast, 2010)
semPaths(bifactor.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor.fit1, whatLabels = "std", layout = "tree")
#Bifactor only with Negative questions protioned out (like model 7 in Marsh, Scalas & Nagengast, 2010)
semPaths(bifactor.negative.fit, whatLabels = "std", layout = "tree")
#Bifactor only with Negative questions protioned out (like model 7 in Marsh, Scalas & Nagengast, 2010)
semPaths(bifactor.positive.fit, whatLabels = "std", layout = "tree")
```
Summaries
```{r}
summary(one.fit, standardized = TRUE, rsquare=TRUE)
summary(two.fit, standardized = TRUE, rsquare=TRUE)
summary(second.fit, standardized = TRUE, rsquare=TRUE)
summary(alt.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.fit1, standardized = TRUE, rsquare=TRUE)
summary(bifactor.negative.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.positive.fit, standardized = TRUE, rsquare=TRUE)
```
Residual correlations
```{r}
correl.1 = residuals(one.fit, type="cor")
correl.1
#View(correl.1$cor)
correl = residuals(two.fit, type="cor")
correl
#View(correl$cor)
correl1 = residuals(second.fit, type="cor")
correl1
#View(correl1$cor)
correl2 = residuals(alt.fit, type="cor")
correl2
#View(correl2$cor)
correl3 = residuals(bifactor.fit, type="cor")
correl3
#View(correl3$cor)
correl4 = residuals(bifactor.fit1, type="cor")
correl4
#View(correl4$cor)
correl5 = residuals(bifactor.negative.fit, type="cor")
correl5
#View(correl5$cor)
correl6 = residuals(bifactor.positive.fit, type="cor")
correl6
#View(correl6$cor)
```
zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels10 = residuals(one.fit, type = "standardized")
zcorrels10$cov
zcorrels = residuals(two.fit, type = "standardized")
zcorrels$cov
#zcorrels1 = residuals(second.fit, type = "standardized")
#zcorrels1$cov
#zcorrels2 = residuals(alt.fit, type = "standardized")
#zcorrels2$cov
#zcorrels3 = residuals(bifactor.fit, type = "standardized")
#zcorrels3$cov
#zcorrels4 = residuals(bifactor1.fit, type = "standardized")
#zcorrels4$cov
zcorrels5 = residuals(bifactor.negative.fit, type = "standardized")
zcorrels5$cov
zcorrels6 = residuals(bifactor.positive.fit, type = "standardized")
zcorrels6$cov
```
Modification indicies
```{r}
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
modindices(two.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(second.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(alt.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.fit1, sort. = TRUE, minimum.value = 3.84)
modindices(bifactor.negative.fit, sort. = TRUE, minimum.value = 3.84)
modindices(bifactor.positive.fit, sort. = TRUE, minimum.value = 3.84)
```
Fit Measures
```{r}
fitmeasures(one.fit)
fitmeasures(two.fit)
fitmeasures(second.fit)
fitmeasures(alt.fit)
fitmeasures(bifactor.fit)
fitmeasures(bifactor.fit1)
fitmeasures(bifactor.negative.fit)
fitmeasures(bifactor.positive.fit)
```
#Create dataset for Target rotation
```{r}
LETTR<-select(LET, LET_1  , LET_2 , LET_3, LET_4 ,  LET_5 , LET_6)
colnames(LETTR) <- c("1","2", "3", "4", "5", "6")
#Target Roration
```{r}
Targ_key <- make.keys(6,list(f1=1:6))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(LETTR,1,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
As two Factor
```{r}
data <- read.csv("/Users/levibrackman/Documents/stats_march_2016/allsurveysYT1_Jan2016.csv")
LETTR2<-select(data, LET_1,	LET_3, LET_5, LET_2,		LET_4, LET_6)
LETTR2$LET_1  <-  6- LETTR2$LET_1
LETTR2$LET_3  <-  6- LETTR2$LET_3
LETTR2$LET_5  <-  6- LETTR2$LET_5
colnames(LETTR2) <- c("1","2", "3", "4", "5", "6")
Targ_key <- make.keys(6,list(f1=1:3, f2=4:6))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
#LETTR2_cor <- corFiml(LETTR2)
out_targetQ <- fa(LETTR2,2,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ

```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```


