---
title: "Perman_CFA"
author: "Levi Brackman"
date: "22 July 2015"
output: html_document
---

From Julie Butler and Peggy Kerns PERMA & EPOCH

Items

1.	How much of the time do you feel you are making progress towards accomplishing your goals? (Acomplishment)

2.	How often do you become absorbed in what you are doing? (Engagement)

3.	In general, how often do you feel joyful? (Positive Emotion)

4.	To what extent do you receive help and support from others when you need it? (Relationship)

5.	In general, how often do you feel anxious? (Negative Emotion)

6.	How often do you achieve the important goals you have set for yourself? (Acomplishment)

7.	In general, how often do you feel positive? (Positive Emotion)

8.	In general, to what extent do you feel excited and interested in things? (Enagagement)	

9.	How lonely do you feel in your daily life? (Lonely -single item)

10.	In general, how often do you feel angry? (Negative Emotion)

11.	To what extent have you been feeling loved? (Relationship)

12.	How often are you able to handle your responsibilities? (Acomplishment)

13.	How satisfied are you with your personal relationships? (Relationship)

14.	In general, how often do you feel sad? (Nagative Emotion)

15.	How often do you lose track of time while doing something you enjoy? (Engagement)

16.	In general, to what extent do you feel contented? (Positive Emotion)

17.	Taking all things together, how happy would you say you are? (Happiness -single item)
```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
```
#loadthedata
```{r}
data <- read.csv("~/Psychometric_study_data/allsurveysT1.csv")
View(data)
```
#create the models
```{r}
seven.model= 'Acomplishment =~ PERMA_1  + PERMA_6 + PERMA_12
              Engagement =~ PERMA_2 +  PERMA_8 + PERMA_15 
              Positive Emotion =~ PERMA_3 + PERMA_7 + PERMA_16
              Relationship =~ PERMA_4 + PERMA_11 + PERMA_13 
              Negative Emotion =~ PERMA_5 + PERMA_10 + PERMA_14
              Lonely =~ PERMA_9  
              Happy =~ PERMA_17'

one.model= 'One =~ PERMA_1  + PERMA_2 + PERMA_3 + PERMA_4 +  PERMA_5 + PERMA_6 + PERMA_7 + PERMA_8 + PERMA_9 + 
PERMA_10 + PERMA_11 + PERMA_12 + PERMA_13 + PERMA_14 + PERMA_15 + PERMA_16  + PERMA_17'
```
#run the models
```{r}
seven.fit=cfa(seven.model, data=data)
one.fit=cfa(one.model, data=data)
```

#create pictures
```{r}
semPaths(seven.fit, whatLabels = "std", layout = "tree")
semPaths(one.fit, whatLabels = "std", layout = "tree")
```
#summaries
```{r}
summary(seven.fit, standardized = TRUE, rsquare=TRUE)
summary(one.fit, standardized = TRUE, rsquare=TRUE)
```
#Residual correlations
```{r}
correl = residuals(seven.fit, type="cor")
correl
View(correl$cor)
correl1 = residuals(one.fit, type="cor")
correl1
View(correl1$cor)
```
#zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels = residuals(seven.fit, type = "standardized")
View(zcorrels$cov)
zcorrels1 = residuals(one.fit, type = "standardized")
View(zcorrels1$cov)
```
#Modification indicies
```{r}
modindices(seven.fit, sort. = TRUE, minimum.value = 3.84)
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
```
#Fit Measures
```{r}
fitmeasures(seven.fit)
fitmeasures(one.fit)
```
#Create dataset for Target rotation
```{r}
PermaTR<-select(data, PERMA_1  , PERMA_6 , PERMA_12, PERMA_2 ,  PERMA_8 , PERMA_15 ,PERMA_3 , PERMA_7 , PERMA_16 , PERMA_4 , PERMA_11 , PERMA_13 , PERMA_5 , PERMA_10 , PERMA_14, PERMA_9  , PERMA_17)
colnames(PermaTR) <- c("1","2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17")

#Target Roration
```{r}
Targ_key <- make.keys(17,list(f1=1:3,f2=4:6, f3=7:9, f4=10:12, f5=13:15, f6=16, f7=17))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(PermaTR,7,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ
