---
title: "RES TR Youth"
author: "Levi Brackman"
date: "28 July 2015"
output: html_document
---

RESILIENCE Items taken from what Herb Marsh has identified as working as part of PERMA.


1.	How quickly do you feel you return to normal after setbacks in your life
2.	How much time does it generally take you to get back to normal when things go wrong in your life
3.	Do you in general quickly get over and recover from significant life difficulties

RES.1  , RES.2  , RES.3


Two factors Consitency and preseverence

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
all_surveys<-read.csv("allsurveysYT1.csv")
all_surveys<-tbl_df(all_surveys)
all_surveys
RES<-select(all_surveys, RES.1  , RES.2  , RES.3)
RES<- data.frame(apply(RES,2, as.numeric))
RES<-tbl_df(RES)
RES
```
One factor Model
```{r}

one.factor = 'RES =~ RES.1 + RES.2 + RES.3 
' 
one.fit=cfa(one.factor, data=RES, missing = "fiml", std.lv = T)
summary(one.fit, standardized = TRUE, rsquare=TRUE)
correl.1 = residuals(one.fit, type="cor")
correl.1
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
fitmeasures(one.fit)

```

```

Target Rotation

```{r, echo=FALSE}
colnames(RES) <- c("1","2", "3")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be RES
Targ_key <- make.keys(3,list(f1=1:3))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
RES_cor <- corFiml(RES) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(RES_cor,1,rotate="TargetQ",n.obs = 1160,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```

