---
title: "SDQ CFA and Target Rotation"
author: "Levi Brackman"
date: "23 July 2015"
output: html_document
---
SDQI
Please select from the list below to what extent you think each / item is true or untrue.
1. I do lots of important things	
2. Overall I am no good	
3. In general, I like being the way I am	
4. Overall I have a lot to be proud of	
5. I can't do anything right	
6. I can do things as well as most other people
7. Other people think I am a good person	
8. A lot of things about me are good	
9. I am as good as most other people	
10. When I do something, I do it well

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
```
#loadthedata
```{r}
data <- read.csv("~/Psychometric_study_data/allsurveysT1.csv")
data<-tbl_df(data)
SDQI<-select(data, SDQI_1, SDQI_2, SDQI_3, SDQI_4, SDQI_5, SDQI_6,SDQI_7, SDQI_8, SDQI_9, SDQI_9.1)
names(SDQI)[10] <- "SDQI_10"
SDQI$SDQI_2  <-  9- SDQI$SDQI_2
SDQI$SDQI_5  <-  9- SDQI$SDQI_5
SDQI<-tbl_df(SDQI)
SDQI

```
#create plots
```{r}
#ggpairs(SDQI, columns = 1:15, title="Big 5 Marsh" )

```
#create the models
```{r}
two.model= ' Factor1  =~ SDQI_1 +  SDQI_2  + SDQI_3 + SDQI_4 + SDQI_5   
              Factor2 =~   SDQI_6 + SDQI_7 + SDQI_8 + SDQI_9  +SDQI_10'       
              

one.model= 'SDQI =~ SDQI_1 +  SDQI_2  + SDQI_3 + SDQI_4 + SDQI_5 + SDQI_6 + SDQI_7 + SDQI_8 + SDQI_9 + SDQI_10'
```
#run the models
```{r}
two.fit=cfa(two.model, data=SDQI)
one.fit=cfa(one.model, data=SDQI)
```

#create pictures
```{r}
semPaths(two.fit, whatLabels = "std", layout = "tree")
semPaths(one.fit, whatLabels = "std", layout = "tree")
```
#summaries
```{r}
summary(two.fit, standardized = TRUE, rsquare=TRUE)
summary(one.fit, standardized = TRUE, rsquare=TRUE)
```
#Residual correlations
```{r}
correl = residuals(two.fit, type="cor")
correl
View(correl$cor)
correl1 = residuals(one.fit, type="cor")
correl1
View(correl1$cor)
```
#zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels = residuals(two.fit, type = "standardized")
View(zcorrels$cov)
zcorrels1 = residuals(one.fit, type = "standardized")
View(zcorrels1$cov)
```
#Modification indicies
```{r}
modindices(two.fit, sort. = TRUE, minimum.value = 3.84)
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
```
#Fit Measures
```{r}
fitmeasures(two.fit)
fitmeasures(one.fit)
```
#Create dataset for Target rotation
```{r}
SDQITR<-select(SDQI, SDQI_1  , SDQI_2 , SDQI_3, SDQI_4 ,  SDQI_5 , SDQI_6 ,SDQI_7 , SDQI_8 , SDQI_9 , SDQI_10)
colnames(SDQITR) <- c("1","2", "3", "4", "5", "6", "7", "8", "9", "10")
#Target Roration
```{r}
Targ_key <- make.keys(10,list(f1=1:5,f2=6:10))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(SDQITR,2,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
As one Factor
```{r}
Targ_key <- make.keys(10,list(f1=1:10))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(SDQITR,1,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA","uniquenesses")]
out_targetQ

```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
