---
title: "CFA & Trarget Rotation MLQ (Youth Only)"
author: "Levi Brackman"
date: "23 July 2015"
output: html_document
---

1.	I understand my life's meaning. 
2.	I am looking for something that makes my life feel meaningful. 
3.	I am always looking to find my life's purpose. 
4.	My life has a clear sense of purpose. 
5.	I have a good sense of what makes my life meaningful. 
6.	I have discovered a satisfying life purpose. 
7.	I am always searching for something that makes my life feel significant. 
8.	I am seeking a purpose or mission for my life. 
9.	My life has no clear purpose. (reverse coded)
10.	I am searching for meaning in my life. 

---

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
```
#loadthedata
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
data<-tbl_df(data)
MLQ<-select(data, MLQ_1, MLQ_2, MLQ_3, MLQ_4, MLQ_5, MLQ_6,MLQ_7, MLQ_8, MLQ_9, MLQ_10)
MLQ$MLQ_9  <-  8- MLQ$MLQ_9
MLQ<-tbl_df(MLQ)
MLQ

```
#create the models
```{r}
two.model= ' Purpose  =~ MLQ_1 +  MLQ_4  + MLQ_5 + MLQ_6 + MLQ_9   
              Searching =~   MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8  +MLQ_10'  #Models two factors:Purpose and Seraching for Purpose     
              

one.model= 'MLQ =~ MLQ_1 +  MLQ_2  + MLQ_3 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_7 + MLQ_8 + MLQ_9 + MLQ_10' #Models as a single purpose factor
```
Second order models
```{r}

second.model = ' Purpose  =~ MLQ_1 +  MLQ_4  + MLQ_5 + MLQ_6 + MLQ_9   
              Searching =~   MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8  +MLQ_10
              MLQ =~ p1*Purpose + p1*Searching
             # MLQ ~~ 1*MLQ
' #Second order models as Purpose being the higher factor made up of Purpose and Searching

```
Bifactor Models (similar to Models 6, 7 & 8 in Marsh, Scalas & Nagengast, 2010)
```{r}

bifactor.negative.model = 'Negative =~ MLQ_9  
                MLQ =~ MLQ_1 +  MLQ_2  + MLQ_3 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_7 + MLQ_8 + MLQ_9 + MLQ_10
                MLQ ~~ 0*Negative
                '#Models bifactor as the negatively worded item as a factor uncorolated with the main factor

bifactor.model1 = 'MLQ =~ MLQ_1 +  MLQ_2  + MLQ_3 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_7 + MLQ_8 + MLQ_9 + MLQ_10
                Purpose  =~ MLQ_1 +  MLQ_4  + MLQ_5 + MLQ_6 + MLQ_9    
              Searching =~   MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8  +MLQ_10
                MLQ ~~ 0*Purpose
                MLQ ~~ 0*Searching
                Purpose~~0*Searching
'#Models bifactor with Searching and Purpose as factors uncorolated with the main factor
bifactor.model1WO9 = 'MLQ =~ MLQ_1 +  MLQ_2  + MLQ_3 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_7 + MLQ_8 + MLQ_10
                Purpose  =~ MLQ_1 +  MLQ_4  + MLQ_5 + MLQ_6    
              Searching =~   MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8  +MLQ_10
                MLQ ~~ 0*Purpose
                MLQ ~~ 0*Searching
                Purpose~~0*Searching
                '
#Models bifactor with Searching and Purpose as factors uncorolated with the main factor leaving negatively worded questions out
```
#run the models
```{r}
two.fit=cfa(two.model, data=MLQ, missing = "fiml")
one.fit=cfa(one.model, data=MLQ, missing = "fiml")
second.fit=cfa(second.model, data=MLQ, missing = "fiml")
bifactor1.fit=cfa(bifactor.model1, data=MLQ, missing = "fiml")
bifactor1WO9.fit=cfa(bifactor.model1WO9, data=MLQ, missing = "fiml")
bifactor.negative.fit=cfa(bifactor.negative.model, data=MLQ, missing = "fiml")
```

#create pictures
```{r}
semPaths(two.fit, whatLabels = "std", layout = "tree")
semPaths(one.fit, whatLabels = "std", layout = "tree")
semPaths(second.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor1.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor1WO9.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor.negative.fit, whatLabels = "std", layout = "tree")
```
#summaries
```{r}
summary(two.fit, standardized = TRUE, rsquare=TRUE)
summary(one.fit, standardized = TRUE, rsquare=TRUE)
summary(second.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor1.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor1WO9.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.negative.fit, standardized = TRUE, rsquare=TRUE)
```
#Residual correlations
```{r}
correl = residuals(two.fit, type="cor")
correl
View(correl$cor)
correl1 = residuals(one.fit, type="cor")
correl1
View(correl1$cor)
correl0 = residuals(second.fit, type="cor")
correl0
View(correl0$cor)
correl4 = residuals(bifactor1.fit, type="cor")
correl4
View(correl4$cor)
correl6 = residuals(bifactor1WO9.fit, type="cor")
correl6
View(correl6$cor)
correl3 = residuals(bifactor.negative.fit, type="cor")
correl3
View(correl3$cor)
```
#zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels = residuals(two.fit, type = "standardized")
View(zcorrels$cov)
zcorrels1 = residuals(one.fit, type = "standardized")
View(zcorrels1$cov)
zcorrel0 = residuals(second.fit, type="cor")
zcorrel0
View(zcorrel0$cor)
correl6 = residuals(bifactor1WO9.fit, type="cor")
correl6
View(correl6$cor)
zcorrel3 = residuals(bifactor.negative.fit, type="cor")
zcorrel3
View(zcorrel3$cor)
zcorrel4 = residuals(bifactor1.fit, type="cor")
zcorrel4
View(zcorrel4$cor)
```
#Modification indicies
```{r}
modindices(two.fit, sort. = TRUE, minimum.value = 3.84)
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(second.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.fit, sort. = TRUE, minimum.value = 3.84)
modindices(bifactor1WO9.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.fitWO9, sort. = TRUE, minimum.value = 3.84)
modindices(bifactor1.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.negative.fit, sort. = TRUE, minimum.value = 3.84)
```
#Fit Measures
```{r}
fitmeasures(two.fit)#Models two factors:Purpose and Seraching for Purpose  
fitmeasures(one.fit) #Models as a single purpose factor
fitmeasures(second.fit)#Second order models as Purpose being the higher factor made up of Purpose and Searching
fitmeasures(bifactor1.fit)#Models bifactor with Searching and Purpose as factors uncorolated with the main factor
fitmeasures(bifactor1WO9.fit)#Models bifactor with Searching and Purpose as factors uncorolated with the main factor leaving negatively worded questions out
fitmeasures(bifactor.negative.fit)#Models bifactor as the negatively worded item as a factor uncorolated with the main factor
```
#Create dataset for Target rotation
```{r}
all_surveys<-read.csv("allsurveysYT1.csv")
MLQ<-select(all_surveys, MLQ_1, MLQ_4,MLQ_5,MLQ_6,MLQ_9,MLQ_2,MLQ_3,MLQ_7,MLQ_8,MLQ_10)
MLQ<- data.frame(apply(MLQ,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

MLQ<-tbl_df(MLQ)
MLQ$MLQ_9  <-  8- MLQ$MLQ_9
MLQ
str(MLQ)
colnames(MLQ) <- c("1","2", "3", "4", "5", "6", "7", "8", "9", "10")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be MLQ
Targ_key <- make.keys(10,list(f1=1:5,f2=6:10))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
MLQ_cor <- corFiml(MLQ)
MLQ_cor
out_targetQ <- fa(MLQ_cor,2,rotate="TargetQ",n.obs = 840,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
---
Droping MLQ_9 which is a reversed scoded question

#Create dataset for Target rotation
```{r}
all_surveys<-read.csv("allsurveysYT1.csv")
MLQ<-select(all_surveys, MLQ_1, MLQ_4,MLQ_5,MLQ_6,MLQ_2,MLQ_3,MLQ_7,MLQ_8,MLQ_10)
MLQ<- data.frame(apply(MLQ,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

MLQ<-tbl_df(MLQ)
MLQ
str(MLQ)
colnames(MLQ) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be MLQ
Targ_key <- make.keys(9,list(f1=1:4,f2=6:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
MLQ_cor <- corFiml(MLQ)
MLQ_cor
out_targetQ <- fa(MLQ_cor,2,rotate="TargetQ",n.obs = 840,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))

