---
title: "CFA & Trarget Rotation MLQ"
author: "Levi Brackman"
date: "March 29, 2016"
output: html_document
---

1.	I understand my life's meaning. 
2.	I am looking for something that makes my life feel meaningful. 
3.	I am always looking to find my life's purpose. 
4.	My life has a clear sense of purpose. 
5.	I have a good sense of what makes my life meaningful. 
6.	I have discovered a satisfying life purpose. 
7.	I am always searching for something that makes my life feel significant. 
8.	I am seeking a purpose or mission for my life. 
9.	My life has no clear purpose. (reverse coded)
10.	I am searching for meaning in my life. 

---

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
library(plyr)
library(xtable)
```
#loadthedata
```{r}
data <- read.csv("/Users/levibrackman/Documents/stats_march_2016/allsurveysYT1_Jan2016.csv")
data<-tbl_df(data)
MLQ<-select(data, MLQ_1, MLQ_2, MLQ_3, MLQ_4, MLQ_5, MLQ_6,MLQ_7, MLQ_8, MLQ_9, MLQ_10)
MLQ$MLQ_9  <-  8- MLQ$MLQ_9
MLQ<-tbl_df(MLQ)
MLQ

```
#create plots
```{r}
#ggpairs(MLQ, columns = 1:15, title="MLQ" )

``
##EFA
##number of factors
##parallal analysis and scree plot
```{r}
parallel<-fa.parallel(MLQ, fm="ml",fa="fa")
#one factors are greater than one Eigenvalue scree plot says there are two factors. Paralel analysis suggests 4 factors
#eigenvalues (kaiser)
parallel$fa.values
#over 1=1, over .7=0
```
#doing aprincipal components analysis to see how many factors there might be using that method
#Deal with NA doing principle componant analysis
```{r}
princomp(na.omit(MLQ), cor = TRUE)
parallel2<-princomp(na.omit(MLQ), cor = TRUE)
summary(parallel2)
plot(parallel2)##results show at least two factors
```
#simple structure
```{r}
twofactor<-fa(MLQ, nfactors=2, rotate="oblimin", fm="ml")
twofactor#not a good fit
1-((twofactor$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))

threefactor<-fa(MLQ, nfactors=3, rotate="oblimin", fm="ml")
threefactor#Still not a great fit. 1, 2, 4, 7, 8 are one factor 3 and 5 seem to be thir own factors and 6 crossloads on all factors. 
1-((threefactor$STATISTIC - threefactor$dof)/(threefactor$null.chisq- threefactor$null.dof))

fourfactor<-fa(MLQ, nfactors=4, rotate="oblimin", fm="ml")
fourfactor#An over fit
1-((fourfactor$STATISTIC - fourfactor$dof)/(fourfactor$null.chisq- fourfactor$null.dof))

fa2latex(fa(MLQ,1, rotate="oblimin", fm="ml"),heading="Table 1. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation of MLQ")

fa2latex(fa(MLQ,2, rotate="oblimin", fm="ml"),heading="Table 2. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation of MLQ")
fa2latex(fa(MLQ,3, rotate="oblimin", fm="ml"),heading="Table 3. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation  of MLQ")
fa2latex(fa(MLQ,4, rotate="oblimin", fm="ml"),heading="Table 4. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation  of MLQ")

```
#create the model1s
```{r}
two.model1= ' Purpose  =~ MLQ_1 +  MLQ_4  + MLQ_5 + MLQ_6 + MLQ_9   
              Searching =~   MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8 + MLQ_10'  #model1s two factors:Purpose and Seraching for Purpose     
              

one.model1= 'MLQ =~ MLQ_1 +  MLQ_2  + MLQ_3 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_7 + MLQ_8 + MLQ_9 + MLQ_10' #model1s as a single purpose factor
```
Second order model1s
```{r}

second.model1 = ' Purpose  =~ MLQ_1 +  MLQ_4  + MLQ_5 + MLQ_6 + MLQ_9   
              Searching =~   MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8  +MLQ_10
              MLQ =~ p1*Purpose + p1*Searching
             # MLQ ~~ 1*MLQ
' #Second order model1s as Purpose being the higher factor made up of Purpose and Searching

```
Bifactor model1s (similar to model1s 6, 7 & 8 in Marsh, Scalas & Nagengast, 2010)
```{r}

bifactor.model1 = 'Purpose  =~ MLQ_1 +  MLQ_4  + MLQ_5 + MLQ_6 + MLQ_9   
              Searching =~   MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8  +MLQ_10
              MLQ =~ MLQ_1 +  MLQ_2  + MLQ_3 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_7 + MLQ_8 + MLQ_9 + MLQ_10
'#model1s bifactor with Searching and Purpose as factors corolated with the main factor

bifactor.model1WO9 = 'Purpose  =~ MLQ_1 +  MLQ_4  + MLQ_5 + MLQ_6  
              Searching =~   MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8  +MLQ_10
              MLQ =~ MLQ_1 +  MLQ_2  + MLQ_3 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_7 + MLQ_8 + MLQ_10
'#model1s bifactor with Searching and Purpose as factors corolated with the main factor leaving negatively worded questions out
```
Bifactor (like model1 7 in Marsh, Scalas & Nagengast, 2010)
```{r}

bifactor.negative.model1 = 'Negative =~ MLQ_9  
                                     MLQ =~ MLQ_1 +  MLQ_2  + MLQ_3 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_7 + MLQ_8 + MLQ_9 + MLQ_10
'#model1s bifactor as the negatively worded item as a factor uncorolated with the main factor

bifactor.model11 = 'MLQ =~ MLQ_1 +  MLQ_2  + MLQ_3 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_7 + MLQ_8 + MLQ_9 + MLQ_10
                Purpose  =~ MLQ_1 +  MLQ_4  + MLQ_5 + MLQ_6 + MLQ_9    
              Searching =~   MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8  +MLQ_10
                MLQ ~~ 0*Purpose
                MLQ ~~ 0*Searching
                Purpose~~0*Searching
'
#model1s bifactor with Searching and Purpose as factors uncorolated with the main factor
bifactor.model11WO9 = 'MLQ =~ MLQ_1 +  MLQ_2  + MLQ_3 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_7 + MLQ_8 + MLQ_10
                Purpose  =~ MLQ_1 +  MLQ_4  + MLQ_5 + MLQ_6    
              Searching =~   MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8  +MLQ_10
                MLQ ~~ 0*Purpose
                MLQ ~~ 0*Searching
                Purpose~~0*Searching
                '
#model1s bifactor with Searching and Purpose as factors uncorolated with the main factor leaving negatively worded questions out
```
#run the model1s
```{r}
two.fit=cfa(two.model1, data=MLQ, missing = "ML", orthogonal = F)
one.fit=cfa(one.model1, data=MLQ)
second.fit=cfa(second.model1, data=MLQ)
bifactor.fit=cfa(bifactor.model1, data=MLQ, missing = "ML", orthogonal = TRUE)
bifactor1.fit=cfa(bifactor.model11, data=MLQ, missing = "ML", orthogonal = TRUE)
bifactorWO9.fit=cfa(bifactor.model1WO9, data=MLQ)
bifactor1WO9.fit=cfa(bifactor.model11WO9, data=MLQ)
bifactor.negative.fit=cfa(bifactor.negative.model1, data=MLQ)
```

#create pictures
```{r}
semPaths(two.fit, whatLabels = "std", layout = "tree")
semPaths(one.fit, whatLabels = "std", layout = "tree")
semPaths(second.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor1.fit, whatLabels = "std", layout = "tree")
semPaths(bifactorWO9.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor1WO9.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor.negative.fit, whatLabels = "std", layout = "tree")
```
#summaries
```{r}
summary(two.fit, standardized = TRUE, rsquare=TRUE)
summary(one.fit, standardized = TRUE, rsquare=TRUE)
summary(second.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor1.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactorWO9.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor1WO9.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.negative.fit, standardized = TRUE, rsquare=TRUE)
```
#Residual correlations
```{r}
correl = residuals(two.fit, type="cor")
correl
#View(correl$cor)
correl1 = residuals(one.fit, type="cor")
correl1
#View(correl1$cor)
correl0 = residuals(second.fit, type="cor")
correl0
#View(correl0$cor)
correl2 = residuals(bifactor.fit, type="cor")
correl2
#View(correl2$cor)
correl4 = residuals(bifactor1.fit, type="cor")
correl4
#View(correl4$cor)
correl5 = residuals(bifactorWO9.fit, type="cor")
correl5
#View(correl5$cor)
correl6 = residuals(bifactor1WO9.fit, type="cor")
correl6
#View(correl6$cor)
correl3 = residuals(bifactor.negative.fit, type="cor")
correl3
#View(correl3$cor)
```
#zscore correlation anything over 1.96 is going to be statistically significant at the .05 level 
```{r}
zcorrels = residuals(two.fit, type = "standardized")
zcorrels
#View(zcorrels$cov)
zcorrels1 = residuals(one.fit, type = "standardized")
#View(zcorrels1$cov)
zcorrel0 = residuals(second.fit, type="cor")
zcorrel0
#View(zcorrel0$cor)
zcorrel2 = residuals(bifactor.fit, type="cor")
zcorrel2
#View(zcorrel2$cor)
zcorrel5 = residuals(bifactorWO9.fit, type="cor")
zcorrel5
#View(zcorrel5$cor)
correl6 = residuals(bifactor1WO9.fit, type="cor")
correl6
#View(correl6$cor)
zcorrel3 = residuals(bifactor.negative.fit, type="cor")
zcorrel3
#View(zcorrel3$cor)
zcorrel4 = residuals(bifactor1.fit, type="cor")
zcorrel4
#View(zcorrel4$cor)
```
#Modification indicies
```{r}
modindices(two.fit, sort. = TRUE, minimum.value = 3.84)
modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(second.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.fit, sort. = TRUE, minimum.value = 3.84)
modindices(bifactor1WO9.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.fitWO9, sort. = TRUE, minimum.value = 3.84)
modindices(bifactor1.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.negative.fit, sort. = TRUE, minimum.value = 3.84)
```
#Fit Measures
```{r}
fitmeasures(two.fit, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#model1s two factors:Purpose and Seraching for Purpose  
fitmeasures(one.fit) #model1s as a single purpose factor
fitmeasures(second.fit, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#Second order model1s as Purpose being the higher factor made up of Purpose and Searching
fitmeasures(bifactor.fit)#model1s bifactor with Searching and Purpose as factors corolated with the main factor
fitmeasures(bifactor1.fit, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#model1s bifactor with Searching and Purpose as factors uncorolated with the main factor
#fitmeasures(bifactorWO9.fit)#model1s bifactor with Searching and Purpose as factors corolated with the main factor leaving negatively worded questions out
fitmeasures(bifactor1WO9.fit)#model1s bifactor with Searching and Purpose as factors uncorolated with the main factor leaving negatively worded questions out
fitmeasures(bifactor.negative.fit)#model1s bifactor as the negatively worded item as a factor uncorolated with the main factor
```
Tables
```{r}
tabel.two.fit<-parameterEstimates(two.fit, zstat = F, pvalue = F, ci = F, 
                   level = 0.95, boot.ci.type = "perc", standardized = T, 
                   fmi = F, remove.system.eq = TRUE, remove.eq = TRUE, 
                   remove.ineq = TRUE, remove.def = T, rsquare = FALSE, 
                   add.attributes = FALSE)
tabel.two.fit<-rename(tabel.two.fit, Factor = lhs, Veriable = rhs, Loadings = std.all)
tabel.two.fit<-select(tabel.two.fit, Factor, op, Veriable, Loadings)
tabel.two.fit<-tabel.two.fit[-c(9:15, 18:26), ]
print(xtable(tabel.two.fit, caption = 'Factor Loadings for Confirmatory Factor Analysis with Lavaan of MLQ, Two Factors MLQ-P and MLQ-S', table.placement =""))
```
#Create dataset for Target rotation
```{r}
all_surveys <- read.csv("/Users/levibrackman/Documents/stats_march_2016/allsurveysYT1_Jan2016.csv")
MLQ<-select(all_surveys, MLQ_1, MLQ_4,MLQ_5,MLQ_6,MLQ_9,MLQ_2,MLQ_3,MLQ_7,MLQ_8,MLQ_10)
MLQ<- data.frame(apply(MLQ,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

MLQ<-tbl_df(MLQ)
MLQ$MLQ_9  <-  8- MLQ$MLQ_9
MLQ
str(MLQ)
colnames(MLQ) <- c("1","2", "3", "4", "5", "6", "7", "8", "9", "10")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be MLQ
Targ_key <- make.keys(10,list(f1=1:5,f2=6:10))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(MLQ,2,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
fa2latex(fa(MLQ,2,rotate="TargetQ", n.obs = 1288, Target=Targ_key), heading="Factor Loadings for Confirmatory Factor Analysis of MLQ, Two Factors MLQ-P and MLQ-S")

```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
---
Droping MLQ_9 which is a reversed scoded question

#Create dataset for Target rotation
```{r}
all_surveys<-read.csv("allsurveys.csv")
MLQ<-select(all_surveys, MLQ_1, MLQ_4,MLQ_5,MLQ_6,MLQ_2,MLQ_3,MLQ_7,MLQ_8,MLQ_10)
MLQ<- data.frame(apply(MLQ,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

MLQ<-tbl_df(MLQ)
MLQ
str(MLQ)
colnames(MLQ) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be MLQ
Targ_key <- make.keys(9,list(f1=1:4,f2=6:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(MLQ,2,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
##Analysis of MLQ-S data with meaning and purpose as two factors
```{r, echo=FALSE}
require(lavaan)
meaning_purposemodel= ' Purpose  =~ MLQ_3 + MLQ_8  
            Meaning =~ MLQ_2 + MLQ_10
                  Purpose ~~ 1*Meaning'
meaning_purposefit=cfa(meaning_purposemodel, data=MLQ, missing = "ML")
# A symmetric matrix is positive definite if all its eigenvalues are (strictly) larger # than zero. So you can test this with: 
eigen(lavInspect(meaning_purposefit, "cov.lv") )$values
#If the negative value is really, really tiny, it is probably safe, and 
# you can ignore the warning. But this is not tiny and shows that the two latent veriables are very highly corrolated. Thus certainly not two factors.
require(semPlot)
semPaths(meaning_purposefit, whatLabels = "std", layout = "tree")
summary(meaning_purposefit, standardized = TRUE, rsquare=TRUE)
correlMP = residuals(meaning_purposefit, type="cor")
correlMP
zcorrelsMP = residuals(meaning_purposefit, type = "standardized")
zcorrelsMP
modindices(meaning_purposefit, sort. = TRUE, minimum.value = 3.84)
Meaning_Purpose_Fit<-fitmeasures(meaning_purposefit, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#Models purpose and meaning
```
One factor meaning in MLQS
```{r, echo=FALSE}
require(lavaan)
purposemodelS= 'Purpose  =~ MLQ_3 + MLQ_8 + MLQ_2 + MLQ_10'
purposemodelSfit=cfa(purposemodelS, data=MLQ, missing = "ML")
# A symmetric matrix is positive definite if all its eigenvalues are (strictly) larger # than zero. So you can test this with: 
eigen(lavInspect(purposemodelSfit, "cov.lv") )$values
#If the negative value is really, really tiny, it is probably safe, and 
# you can ignore the warning. But this is not tiny and shows that the two latent veriables are very highly corrolated. Thus certainly not two factors.
require(semPlot)
semPaths(purposemodelSfit, whatLabels = "std", layout = "tree")
summary(purposemodelSfit, standardized = TRUE, rsquare=TRUE)
correlMP = residuals(purposemodelSfit, type="cor")
correlMP
zcorrelsMP = residuals(purposemodelSfit, type = "standardized")
zcorrelsMP
modindices(purposemodelSfit, sort. = TRUE, minimum.value = 3.84)
onefactorfit<-fitmeasures(purposemodelSfit, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#Models purpose and meaning
```
Table of fit measure MLS-S
```{r}
onefactorfit<-data.frame(onefactorfit)
meaning_purposefit<-data.frame(Meaning_Purpose_Fit)
all<-bind_cols(names, onefactorfit, meaning_purposefit)
tableall_fit_measures<-rename(all, Fit_Measure = c..Chisq....DF....P.Value....CFI....TLI....RMSEA....RMSEA.ci.upper...,  'One Factor Model' =  onefactorfit , 'Meaning Purpose Model' = Meaning_Purpose_Fit)
tableall_fit_measures
xtable(tableall_fit_measures)
```
##Analysis of Purpsoe Navigator data with purpose as one factors
```{r, echo=FALSE}
require(lavaan)
purposemodel= ' Purpose  =~ MLQ_1 + MLQ_5 + MLQ_4 + MLQ_6 + MLQ_9'
purposefit=cfa(purposemodel, data=MLQ, missing = "ML")
require(semPlot)
semPaths(purposefit, whatLabels = "std", layout = "tree")
summary(purposefit, standardized = TRUE, rsquare=TRUE)
correlMP = residuals(purposefit, type="cor")
correlMP
zcorrelsMP = residuals(purposefit, type = "standardized")
zcorrelsMP
modindices(purposefit, sort. = TRUE, minimum.value = 3.84)
onefactorfit<-fitmeasures(purposefit, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#Models purpose and meaning
```

##Compare with other MLQ-S Menaing and Purpose
```{r}

purposemodelMLQ =  'Purpose  =~ MLQ_3 + MLQ_8  
            Meaning =~ MLQ_2 + MLQ_7 + MLQ_10
            Global =~ Purpose + Meaning'
purposefit1=cfa(purposemodelMLQ, data=MLQ, missing = "ML", std.lv = TRUE)
semPaths(purposefit1, whatLabels = "std", layout = "tree")
summary(purposefit1, standardized = TRUE, rsquare=TRUE)
correlMP = residuals(purposefit1, type="cor")
correlMP
zcorrelsMP = residuals(purposefit1, type = "standardized")
zcorrelsMP
modindices(purposefit1, sort. = TRUE, minimum.value = 3.84)
options(scipen=999)
fitmeasures(purposefit1, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#Models purpose and meaning
```

##Compare with other MLQ-p Meanign and Purpose second order
```{r}

purposemodelMLQSecond =  'Purpose  =~ MLQ_1 + MLQ_5  
            Meaning =~ MLQ_4 + MLQ_6 + MLQ_9
            Global =~ Meaning + Purpose'
purposefitsecond=cfa(purposemodelMLQSecond, data=MLQ, missing = "ML", std.lv = TRUE)
semPaths(purposefitsecond, whatLabels = "std", layout = "tree")
summary(purposefitsecond, standardized = TRUE, rsquare=TRUE)
correlMP = residuals(purposefitsecond, type="cor")
correlMP
zcorrelsMP = residuals(purposefitsecond, type = "standardized")
zcorrelsMP
modindices(purposefitsecond, sort. = TRUE, minimum.value = 3.84)
options(scipen=999)
PM_MLQ_p_second_order<-fitmeasures(purposefitsecond, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#Models purpose and meaning
tabel.fit2<-parameterEstimates(purposefitsecond, zstat = F, pvalue = F, ci = F, 
                   level = 0.95, boot.ci.type = "perc", standardized = T, 
                   fmi = F, remove.system.eq = TRUE, remove.eq = TRUE, 
                   remove.ineq = TRUE, remove.def = T, rsquare = FALSE, 
                   add.attributes = FALSE)
tabel.fit2<-rename(tabel.fit2, Factor = lhs, Veriable = rhs, Loadings = std.all)
tabel.fit2<-select(tabel.fit2, Factor, op, Veriable, Loadings)
tabel.fit2<-tabel.fit2[-c(9:15, 18:26), ]
print(xtable(tabel.fit2, caption = 'Factor Loadings for Confirmatory Factor Analysis with Lavaan of MLQ-P Second Prder Purpose and Meanign Factors', table.placement =""))
#DOES NOT WORK
```
```
##Analysis of Purpsoe Navigator data with meaning and purpose as two factors
```{r, echo=FALSE}
require(lavaan)
meaning_purposemodel= ' Purpose  =~ MLQ_1 + MLQ_5  
            Meaning =~ MLQ_4 + MLQ_6 + MLQ_9'
meaning_purposefit=cfa(meaning_purposemodel, data=MLQ, missing="ML")
require(semPlot)
semPaths(meaning_purposefit, whatLabels = "std", layout = "tree")
summary(meaning_purposefit, standardized = TRUE, rsquare=TRUE)
correlMP = residuals(meaning_purposefit, type="cor")
correlMP
zcorrelsMP = residuals(meaning_purposefit, type = "standardized")
zcorrelsMP
modindices(meaning_purposefit, sort. = TRUE, minimum.value = 3.84)
PM_MLQ_p<-fitmeasures(meaning_purposefit, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#Models purpose and meaning
#Table
tabel.fit3<-parameterEstimates(meaning_purposefit, zstat = F, pvalue = F, ci = F, 
                   level = 0.95, boot.ci.type = "perc", standardized = T, 
                   fmi = F, remove.system.eq = TRUE, remove.eq = TRUE, 
                   remove.ineq = TRUE, remove.def = T, rsquare = FALSE, 
                   add.attributes = FALSE)
tabel.fit3<-rename(tabel.fit3, Factor = lhs, Veriable = rhs, Loadings = std.all)
tabel.fit3<-select(tabel.fit3, Factor, op, Veriable, Loadings)
tabel.fit3<-tabel.fit3[-c(9:15, 18:26), ]
print(xtable(tabel.fit3, caption = 'Factor Loadings for Confirmatory Factor Analysis with Lavaan of MLQ-P, Two Factors of meaning and purpose factors', table.placement =""))


```
##Analysis of Purpsoe Navigator data with purpose as one factors
```{r, echo=FALSE}
require(lavaan)
purposemodel= ' Purpose  =~ MLQ_1 + MLQ_5 + MLQ_4 + MLQ_6 + MLQ_9'
purposefit=cfa(purposemodel, data=MLQ)
require(semPlot)
semPaths(purposefit, whatLabels = "std", layout = "tree")
summary(purposefit, standardized = TRUE, rsquare=TRUE)
correlMP = residuals(purposefit, type="cor")
correlMP
zcorrelsMP = residuals(purposefit, type = "standardized")
zcorrelsMP
modindices(purposefit, sort. = TRUE, minimum.value = 3.84)
P1FactorMLQ_p<-fitmeasures(purposefit, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#Models purpose and meaning

tabel.fit4<-parameterEstimates(purposefit, zstat = F, pvalue = F, ci = F, 
                   level = 0.95, boot.ci.type = "perc", standardized = T, 
                   fmi = F, remove.system.eq = TRUE, remove.eq = TRUE, 
                   remove.ineq = TRUE, remove.def = T, rsquare = FALSE, 
                   add.attributes = FALSE)
tabel.fit4<-rename(tabel.fit4, Factor = lhs, Veriable = rhs, Loadings = std.all)
tabel.fit4<-select(tabel.fit4, Factor, op, Veriable, Loadings)
tabel.fit4<-tabel.fit4[-c(9:15, 18:26), ]
print(xtable(tabel.fit4, caption = 'Factor Loadings for Confirmatory Factor Analysis with Lavaan of MLQ-P, One Purpose Factor', table.placement =""))
```

##Compare with other MLQ from large youth dataset with negatively worded item
```{r}

purposemodelMLQ =  'Purpose  =~ MLQ_1 + MLQ_5  
            Meaning =~ MLQ_4 + MLQ_6 + MLQ_9
            Global =~ Purpose + Meaning'
purposefit1=cfa(purposemodelMLQ, data=MLQ, missing = "ML", std.lv = TRUE)
semPaths(purposefit1, whatLabels = "std", layout = "tree")
summary(purposefit1, standardized = TRUE, rsquare=TRUE)
correlMP = residuals(purposefit1, type="cor")
correlMP
zcorrelsMP = residuals(purposefit1, type = "standardized")
zcorrelsMP
modindices(purposefit1, sort. = TRUE, minimum.value = 3.84)
options(scipen=999)
PMSecondMLQ_p<-fitmeasures(purposefit1, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#Models purpose and meaning
onefactorfit<-data.frame(onefactorfit)
PM_MLQ_p_second_order<-data.frame(PM_MLQ_p_second_order)
PM_MLQ_p<-data.frame(PM_MLQ_p)
all<-bind_cols(names, onefactorfit, PM_MLQ_p, PM_MLQ_p_second_order)
tableall_fit_measures<-rename(all, Fit_Measure = c..Chisq....DF....P.value....CFI....TLI....RMSEA....RMSEA.ci.lower...,  MLQpurpose_fit =  onefactorfit , meaningpurpose_fit = PM_MLQ_p, purpose_fit_secon_order=PM_MLQ_p_second_order)
tableall_fit_measures


```

##Try to see if I can get meaning and purpose into entire MLQ-S and MLQ-P
```{r}

purposemodelMLQbifactor =  'Purpose  =~ MLQ_1 + MLQ_5  
            Meaning =~ MLQ_4 + MLQ_6 + MLQ_9
            Global =~ MLQ_1 + MLQ_5  + MLQ_4 + MLQ_6 + MLQ_9'
purposefitBi=cfa(purposemodelMLQbifactor, data=MLQ, missing = "ML", orthogonal = TRUE)
semPaths(purposefitBi, whatLabels = "std", layout = "tree")
summary(purposefitBi, standardized = TRUE, rsquare=TRUE)
correlMP = residuals(purposefitBi, type="cor")
correlMP
zcorrelsMP = residuals(purposefitBi, type = "standardized")
zcorrelsMP
modindices(purposefitBi, sort. = TRUE, minimum.value = 3.84)
options(scipen=999)
fitmeasures(purposefitBi, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#Models purpose and meaning
#DOES NOT WORK
```
```

##Try to see if I can get meaning and purpose into entire MLQ-S and MLQ-P
```{r}

purposemodelMLQbifactor =  'Purpose  =~ MLQ_1 + MLQ_2 + MLQ_5 + MLQ_10  
            Meaning =~ MLQ_3 + MLQ_4 + MLQ_6 + MLQ_8 + MLQ_9 
            #Global =~ MLQ_1 + MLQ_5  + MLQ_4 + MLQ_6 + MLQ_9
            '
purposefitBi=cfa(purposemodelMLQbifactor, data=MLQ, missing = "ML", orthogonal = TRUE)
semPaths(purposefitBi, whatLabels = "std", layout = "tree")
summary(purposefitBi, standardized = TRUE, rsquare=TRUE)
correlMP = residuals(purposefitBi, type="cor")
correlMP
zcorrelsMP = residuals(purposefitBi, type = "standardized")
zcorrelsMP
modindices(purposefitBi, sort. = TRUE, minimum.value = 3.84)
options(scipen=999)
fitmeasures(purposefitBi, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))#Models purpose and meaning
parameterEstimates(purposefitBi)
tabel.fitPM<-parameterEstimates(purposefitBi, zstat = F, pvalue = F, ci = F, 
                   level = 0.95, boot.ci.type = "perc", standardized = T, 
                   fmi = F, remove.system.eq = TRUE, remove.eq = TRUE, 
                   remove.ineq = TRUE, remove.def = T, rsquare = FALSE, 
                   add.attributes = FALSE)
tabel.fitPM<-rename(tabel.fitPM, Factor = lhs, Veriable = rhs, Loadings = std.all)
tabel.fitPM<-select(tabel.fitPM, Factor, op, Veriable, Loadings)
tabel.fitPM<-tabel.fitPM[-c(10:32), ]

xtable(tabel.fitPM, caption = 'Factor Loadings for Confirmatory Factor Analysis with Lavaan of MLQ, Two Factors: Meaning and Purpose', table.placement ="")
```{r}
##Table of Fit Measures

Colunm names explained:

* MLQ_With_9 is the large Youth data frame from the study which includes MLQ_9 a negatively worded item
* Meaning_Purpose_PN is the data from the purpose navigator with two factors
* Purpose_PN is the data from the purpose navigator with just one factor

**It seems that when we have a positive question instead of the negatively worded one we get a much better fit for the data.**
```{r, echo=F}
names<- data.frame(c("Chisq", "DF", "P-value", "CFI", "TLI", "RMSEA", "RMSEA ci lower", "RMSEA ci upper", "SRMR"))
onefactorfit<-data.frame(onefactorfit)
PM_MLQ_p_second_order<-data.frame(PM_MLQ_p_second_order)
PM_MLQ_p<-data.frame(PM_MLQ_p)
all<-bind_cols(names, onefactorfit, PM_MLQ_p, PM_MLQ_p_second_order)
tableall_fit_measures<-rename(all, Fit_Measure = c..Chisq....DF....P.value....CFI....TLI....RMSEA....RMSEA.ci.lower...,  MLQpurpose_fit =  onefactorfit , meaningpurpose_fit = PM_MLQ_p, purpose_fit_secon_order=PM_MLQ_p_second_order)
tableall_fit_measures
xtable(tableall_fit_measures)

```
Traget rotation for meanign and purpose as two factors
```{r}
```{r}
all_surveys <- read.csv("/Users/levibrackman/Documents/stats_march_2016/allsurveysYT1_Jan2016.csv")
MLQ<-select(all_surveys, MLQ_2, MLQ_7, MLQ_10,MLQ_3,MLQ_8)
MLQ<- data.frame(apply(MLQ,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

MLQ<-tbl_df(MLQ)
#MLQ$MLQ_9  <-  8- MLQ$MLQ_9
MLQ
str(MLQ)
colnames(MLQ) <- c("1","2", "3", "4", "5")#, "6", "7", "8", "9", "10")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be MLQ
Targ_key <- make.keys(5,list(f1=1:3,f2=4:4))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(MLQ,2,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
fa2latex(fa(MLQ,2,rotate="TargetQ", n.obs = 1288, Target=Targ_key), heading="Factor Loadings for Confirmatory Factor Analysis of MLQ, Two Factors MLQ-P and MLQ-S")

```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
Traget rotation for meanign and purpose as two factors using "searching" and "Presence"
```{r}
```{r}
all_surveys <- read.csv("/Users/levibrackman/Documents/stats_march_2016/allsurveysYT1_Jan2016.csv")
MLQ<-select(all_surveys, MLQ_1, MLQ_2, MLQ_5, MLQ_10, MLQ_3, MLQ_4, MLQ_6, MLQ_8, MLQ_9)
MLQ<- data.frame(apply(MLQ,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

MLQ<-tbl_df(MLQ)
MLQ$MLQ_9  <-  8- MLQ$MLQ_9
MLQ
str(MLQ)
colnames(MLQ) <- c("MLQ1_MP","MLQ2_MS", "MLQ5_MP", "MLQ10_MS", "MLQ3_PS", "MLQ4_PP", "MLQ6_PP", "MLQ8_PS", "MLQ9_PP")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be MLQ
Targ_key <- make.keys(9,list(f1=1:4,f2=5:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(MLQ, 2, rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
fa2latex(fa(MLQ,2,rotate="TargetQ", n.obs = 1288, Target=Targ_key), heading="Factor Loadings for Confirmatory Factor Analysis of MLQ, Two Factors MLQ-P and MLQ-S")

```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```

#Convergant  analysis, Discriminant  analysis
```{r}
data <- read.csv("/Users/levibrackman/Documents/stats_march_2016/allsurveysYT1_Jan2016.csv")
data$MLQ_9  <-  8- data$MLQ_9

ConvergantMLQ.model = 'MLQ P =~  MLQ_1 + MLQ_4 + MLQ_5 + MLQ_6 + MLQ_9
                            MLQ S  =~  MLQ_2 + MLQ_3 + MLQ_7 + MLQ_8 + MLQ_10
                            Feeling Purpose Now =~ APSI_1 + APSI_2 + APSI_5
                            Future goals =~ APSI_4 + APSI_7 + APSI_8
                           Purpose =~ Feeling Purpose Now + Future goals
                             English =~ ASDQII_1 + ASDQII_2 + ASDQII_3 + ASDQII_4 + ASDQII_5
                              Math =~ ASDQII_6 + ASDQII_7 + ASDQII_8 + ASDQII_9 + ASDQII_10
                             Science =~  ASDQII_11 + ASDQII_12 + ASDQII_13 + ASDQII_14 + ASDQII_15
                            Subjects =~  ASDQII_16 + ASDQII_17 + ASDQII_18 + ASDQII_19 + ASDQII_20
                            '
ConvergantMLQ.fit=cfa(ConvergantMLQ.model, data=data, missing = "ML", std.lv = TRUE)
semPaths(ConvergantMLQ.fit, whatLabels = "std", layout = "tree")
summary(ConvergantMLQ.fit, standardized = TRUE, rsquare=TRUE)
correl1 = residuals(ConvergantMLQ.fit, type="cor")
correl1
correl2 = residuals(ConvergantMLQ.fit, type="standardized")
correl2$cov
modindices(ConvergantMLQ.fit, sort. = TRUE, minimum.value = 3.84)
summary(ConvergantMLQ.fit, standardized=TRUE, rsquare=TRUE)
fitmeasures(ConvergantMLQ.fit, c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr")) #Models as a single purpose factor
inspect(ConvergantMLQ.fit,what="std")
fitted(ConvergantMLQ.fit)
co1<-cov2cor(inspect(ConvergantMLQ.fit, "coefficients")$psi) 
co1
#res.table<-xtable(parameterEstimates(ConvergantMLQ.fit, standardized=TRUE), caption = 'Table 20. Factor Loadings for Convergant Analysis with MLQ using Lavaan of APSIr', table.placement ="")
#print(res.table, scalebox=0.5, caption.placement = "top")

tabel.fit6<-parameterEstimates(ConvergantMLQ.fit, zstat = F, pvalue = F, ci = F, 
                   level = 0.95, boot.ci.type = "perc", standardized = T, 
                   fmi = F, remove.system.eq = TRUE, remove.eq = TRUE, 
                   remove.ineq = TRUE, remove.def = T, rsquare = FALSE, 
                   add.attributes = FALSE)
tabel.fit6<-rename(tabel.fit6, Factor = lhs, Veriable = rhs, Loadings = std.all)
tabel.fit6<-select(tabel.fit6, Factor, op, Veriable, Loadings)
tabel.fit6<-tabel.fit6[-c(39:74, 105:149), ]

xtable(tabel.fit6, caption = 'Factor Loadings for Convergant Analysis of APSI with MLQ-Present and MLQ Searching using Lavaan', table.placement ="")
```

