---
title: "APSI EFA, CFA"
author: "Levi Brackman"
date: "4 August 2015"
output: html_document
---
---

```{r}
##load packages
library(psych)
library(GPArotation)
library(plyr)
library(dplyr)
# data preparation
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
APSI<-select(data, APSI_1, APSI_2,  APSI_3,  APSI_4,  APSI_5,  APSI_6, APSI_7, APSI_8)
APSI$APSI_6  <-  6- APSI$APSI_6

APSI<- data.frame(apply(APSI,2, as.numeric))
APSI<-tbl_df(APSI)
APSI
str(APSI)
colnames(APSI) <- c("1","2","3","4","5","6","7","8")
#APSI<- APSI[complete.cases(APSI[,]),]
##EFA
##number of factors
##parallal analysis and scree plot
parallel<-fa.parallel(APSI, fm="ml",fa="fa")
#two factors are greater than one Eigenvalue scree plot says there are two factors. Paralel analysis suggests 4 factors
#eigenvalues (kaiser)
parallel$fa.values
#over 1=2, over .7=2
#doign aprincipal components analysis to see how many factors there might be using that method
#Deal with NA doing principle componant analysis
princomp(na.omit(APSI), cor = TRUE)
parallel2<-princomp(na.omit(APSI), cor = TRUE)
summary(parallel2)
plot(parallel2)##results show at least two factors
#simple structure
twofactor<-fa(APSI, nfactors=2, rotate="oblimin", fm="ml")
twofactor
threefactor<-fa(APSI, nfactors=3, rotate="oblimin", fm="ml")
threefactor
fourfactor<-fa(APSI, nfactors=4, rotate="oblimin", fm="ml")
fourfactor
fivefactor<-fa(APSI, nfactors=5, rotate="oblimin", fm="ml")
fivefactor
#1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33
 
#Create dataset for Target rotation
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
APSI<-select(data, APSI_1, APSI_2,  APSI_3,  APSI_4,  APSI_5,  APSI_6, APSI_7, APSI_8)
APSI$APSI_6  <-  6- APSI$APSI_6

APSI<- data.frame(apply(APSI,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

APSI<-tbl_df(APSI)
APSI
str(APSI)
colnames(APSI) <- c("1","2","3","4","5","6","7","8")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be APSI
Targ_key <- make.keys(8,list(f1=1:8))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
APSI_cor <- corFiml(APSI)
out_targetQ <- fa(APSI_cor,1,rotate="TargetT",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
summary(out_targetQ)
print(out_targetQ, Table=TRUE)
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
Two factor model
```{r}
#Create dataset for Target rotation
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
APSI<-select(data, APSI_1, APSI_2,  APSI_4,  APSI_5,  APSI_7,  APSI_8, APSI_3, APSI_6)
APSI$APSI_6  <-  6- APSI$APSI_6

APSI<- data.frame(apply(APSI,2, as.numeric))

APSI<-tbl_df(APSI)
APSI
str(APSI)
colnames(APSI) <- c("1","2","3","4","5","6","7","8")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be APSI
Targ_key <- make.keys(8,list(f1=1:6, f2=7:8))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
APSI_cor <- corFiml(APSI)
out_targetQ <- fa(APSI,2,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```