---
title: "APSI with MI March 25 2015"
author: "Levi Brackman"
date: "March 8, 2015"
output: word_document
---
Loading the dataset
```{r}
data.test4 <- read.csv("~/Final_Adult_Study_R_Docs/adult_study011615.csv")
# Load the psych package
library(psych)
items <- grep("APSI[0-8]", names(data.test4), value=TRUE)
scaleKey <- c(1, 1, 1, 1, 1, -1, 1, 1)
data.test4[,items] <- apply(data.test4[,items], 2, as.numeric)
data.test4$meanAPSI <- scoreItems(scaleKey, items = data.test4[, items], delete = FALSE)$score
library(reshape2); library(car); library(Amelia);library(mitools);library(nlme);library(predictmeans)
#Remove the meanAPSI and ID Group and wave from data.test4 and create a new #dataset with only those variables.
data <- data.test4[,c("ID", "GROUP", "wave", "meanAPSI")]
#Use dcast to cnage from long-format data to wide format data
data <- dcast(data, ID + GROUP ~ wave, mean, value.var = "meanAPSI")
# Changing all NaNs to NA
data[,3:5] <- apply(data[,3:5],2,function(x) recode(x, "NaN = NA") )
```
Unsing the mapply function we create a new data set with ID Group baseline meanAPSI and wave 2 and 3 of meanAPSI. So we have a Baseline, which is Time 1 (placed in column 3 one on top of the other) to compare to both Time 2 and 3 (placed in column 4 one on top of the other).  In the next line of code we then create a separate column called “wave” which calls the first 89 (which compares Time 2 to Baseline) “wave 1” and then the second 89 we call “wave 2” which compares Time 3 to Baseline.  In the third line of code we add names to the new columns of the dataset. 
```{r}
data2 <- as.data.frame(mapply(c,data[,1:4], data[,c(1:3,5)]))
data2$wave <- rep(1:2, each=89)
names(data2) <- c("ID", "GROUP", "BASELINE", "meanAPSI", "WAVE")
```
Intention to treat model (ITT) where we keep the cases who dropped out and did not complete the study (http://en.wikipedia.org/wiki/Intention-to-treat_analysis).
```{r}
data2[which(data2$GROUP ==2), "GROUP"] <- 1
```
#Make GROUP and ID a factor
```{r}
data2$GROUP <-as.factor(data2$GROUP)
data2$ID <-as.factor(data2$ID)
```
Imputing missing data 
```{r}
MI <- amelia(data2, 50, idvars = c("ID"), ords = "GROUP")
```
Creating new dataset with missing data imputed
```{r}
data(MI$imputations)
allimplogreg<-lapply(MI$imputations,function(X) {lme(meanAPSI ~ GROUP * WAVE + BASELINE, random = ~1 | ID, data = X, method = "ML", na.action = "na.omit")})
betas<-MIextract(allimplogreg, fun=fixef)
vars<-MIextract(allimplogreg, fun=vcov)
summary<-summary(MIcombine(betas,vars))
library(pander)
```
Table
```{r, results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
pandoc.table(summary, split.table=100000)

```
Check results with Imputations using Zelig
```{r}

library("Zelig")
zelig.fit <- zelig(meanAPSI ~ GROUP * WAVE + BASELINE, random = ~1 | ID, data = MI$imputations,  model = "ls", cite = FALSE)
summary(zelig.fit)
summary1<-summary(zelig.fit)
```
Table with p-values
```{r, results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
pandoc.table(coefficients(summary1, split.table=100000))
```
Check assumptions with Random Computations
```{r}
data1=MI$imputations[[1]]
library("Zelig")
zelig.fitdata1 <- zelig(meanAPSI ~ GROUP * WAVE + BASELINE, random = ~1 | ID, data = data1,  model = "ls", cite = FALSE)
summary(zelig.fitdata1)
summary1<-summary(zelig.fit)
```
Table with p-values
```{r, results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
pandoc.table(coefficients(summary1, split.table=100000))
```
Describe the meanAPSI variable by the GROUP variable
```{r}
describeBy(data1[,3:4], group = data1$GROUP)
```
Create a plot that visualizes meanAPSI variable by the GROUP variable
```{r}
library(ggplot2)
library(influence.ME)
```
Take a look at the residuals
```{r}
residual <- lm(meanAPSI ~ BASELINE, data=data1)$residual
```
Plot the residuals to see that they are random
```{r}
plot(density(residual))# A density plot
qqnorm(residual) # A quantile normal plot to checking normality
qqline(residual)
```
Checking the different between intervention and control groups residuals. This allows us to control for individual unsystematic differences.  
```{r}
data2$residual <- NA
sel1 <- which(!is.na(data1$meanAPSI)) 
sel2 <- which(!is.na(data1$BASELINE))
data1$residual[intersect(sel1,sel2)] <- residual
qplot(GROUP, meanAPSI, data=data1, geom="boxplot")
```
Plot of the difference between intervention and control groups.
```{r}
qplot(GROUP, residual, data=data1, geom="boxplot")
```
Two way repeated measures
========================================================
Graphing the Two-Way Interaction. Both meanAPSI and the Residuals
```{r}
# Load the nlme package
library(nlme)
with(data1, boxplot(meanAPSI ~ WAVE + GROUP))
with(data1, boxplot(residual ~ WAVE + GROUP))
```
<center><font size="3" color="blue">Linear Mixed-Effects Model</font><center> Comparing Basline to Wave 2 and 3 by Group.
```{r}             
fullModeldata1 <- lme(meanAPSI ~ GROUP * WAVE + BASELINE, random = ~1 | ID, data = data1, method = "ML", na.action = "na.omit")
```
#Cooks Distence
```{r}
CookD(fullModeldata1)
```
#Plot Cook's distance:
```{r}
plot(fullModeldata1, which="cook")
```
Check results on this random Imputation model
<center><font size="6" color="green">Results</font><center>
<center><p><b>Explanation of significance:</b></p></center>
We asses the significance of our models by comparing them from the baseline model using the anova() function.<br>
(Intercept): Where everything is 0<br>
GROUP1: Is there a difference between group. If it is significant than there is a difference and the treatment had an effect.<br> 
WAVE: Asseses whether the effects gets bigger beteen time 2 and 3 (does not have to be significant)<br>
BASELINE: Should not be significant. If it is then it shows that there is a difference between groups before the treatment.<br>
GROUP1:WAVE: If this is significant then it means that the effect was either fleeting or it happened after the treatment i.e. between time 2 and 3. 
```{r}
summary(fullModeldata1)
```
Another random imputation
```{r}
data10=MI$imputations[[10]]
library("Zelig")
zelig.fitdata10 <- zelig(meanAPSI ~ GROUP * WAVE + BASELINE, random = ~1 | ID, data = data10,  model = "ls", cite = FALSE)
summary(zelig.fitdata10)
```
Describe the meanAPSI variable by the GROUP variable
```{r}
describeBy(data10[,3:4], group = data10$GROUP)
```
Create a plot that visualizes meanAPSI variable by the GROUP variable
```{r}
library(ggplot2)
library(influence.ME)
```
Take a look at the residuals
```{r}
residual <- lm(meanAPSI ~ BASELINE, data=data10)$residual
```
Plot the residuals to see that they are random
```{r}
plot(density(residual))# A density plot
qqnorm(residual) # A quantile normal plot to checking normality
qqline(residual)
```
Checking the different between intervention and control groups residuals. This allows us to control for individual unsystematic differences.  
```{r}
data2$residual <- NA
sel1 <- which(!is.na(data10$meanAPSI)) 
sel2 <- which(!is.na(data10$BASELINE))
data10$residual[intersect(sel1,sel2)] <- residual
qplot(GROUP, meanAPSI, data=data10, geom="boxplot")
```
Plot of the difference between intervention and control groups.
```{r}
qplot(GROUP, residual, data=data10, geom="boxplot")
```
Two way repeated measures
========================================================
Graphing the Two-Way Interaction. Both meanAPSI and the Residuals
```{r}
# Load the nlme package
library(nlme)
with(data10, boxplot(meanAPSI ~ WAVE + GROUP))
with(data10, boxplot(residual ~ WAVE + GROUP))
```
<center><font size="3" color="blue">Linear Mixed-Effects Model</font><center> Comparing Basline to Wave 2 and 3 by Group.
```{r}             
fullModeldata10 <- lme(meanAPSI ~ GROUP * WAVE + BASELINE, random = ~1 | ID, data = data10, method = "ML", na.action = "na.omit")
```
#Cooks Distence
```{r}
CookD(fullModeldata10)
```
#Plot Cook's distance:
```{r}
plot(fullModeldata10, which="cook")
```
Check results on this random Imputation model
<center><font size="6" color="green">Results</font><center>
<center><p><b>Explanation of significance:</b></p></center>
We asses the significance of our models by comparing them from the baseline model using the anova() function.<br>
(Intercept): Where everything is 0<br>
GROUP1: Is there a difference between group. If it is significant than there is a difference and the treatment had an effect.<br> 
WAVE: Asseses whether the effects gets bigger beteen time 2 and 3 (does not have to be significant)<br>
BASELINE: Should not be significant. If it is then it shows that there is a difference between groups before the treatment.<br>
GROUP1:WAVE: If this is significant then it means that the effect was either fleeting or it happened after the treatment i.e. between time 2 and 3. 
```{r}
summary(fullModeldata10)
```
Another random imputation
```{r}

data15=MI$imputations[[15]]
library("Zelig")
zelig.fitdata15 <- zelig(meanAPSI ~ GROUP * WAVE + BASELINE, random = ~1 | ID, data = data15,  model = "ls", cite = FALSE)
summary(zelig.fitdata15)
```
Describe the meanAPSI variable by the GROUP variable
```{r}
describeBy(data15[,3:4], group = data15$GROUP)
```
Create a plot that visualizes meanAPSI variable by the GROUP variable
```{r}
library(ggplot2)
library(influence.ME)
```
Take a look at the residuals
```{r}
residual <- lm(meanAPSI ~ BASELINE, data=data15)$residual
```
Plot the residuals to see that they are random
```{r}
plot(density(residual))# A density plot
qqnorm(residual) # A quantile normal plot to checking normality
qqline(residual)
```
Checking the different between intervention and control groups residuals. This allows us to control for individual unsystematic differences.  
```{r}
data2$residual <- NA
sel1 <- which(!is.na(data15$meanAPSI)) 
sel2 <- which(!is.na(data15$BASELINE))
data15$residual[intersect(sel1,sel2)] <- residual
qplot(GROUP, meanAPSI, data=data15, geom="boxplot")
```
Plot of the difference between intervention and control groups.
```{r}
qplot(GROUP, residual, data=data15, geom="boxplot")
```
Two way repeated measures
========================================================
Graphing the Two-Way Interaction. Both meanAPSI and the Residuals
```{r}
# Load the nlme package
library(nlme)
with(data15, boxplot(meanAPSI ~ WAVE + GROUP))
with(data15, boxplot(residual ~ WAVE + GROUP))
```
<center><font size="3" color="blue">Linear Mixed-Effects Model</font><center> Comparing Basline to Wave 2 and 3 by Group.
```{r}             
fullModeldata15 <- lme(meanAPSI ~ GROUP * WAVE + BASELINE, random = ~1 | ID, data = data15, method = "ML", na.action = "na.omit")
```
#Cooks Distence
```{r}
CookD(fullModeldata15)
```
#Plot Cook's distance:
```{r}
plot(fullModeldata15, which="cook")
```
Check results on this random Imputation model
<center><font size="6" color="green">Results</font><center>
<center><p><b>Explanation of significance:</b></p></center>
We asses the significance of our models by comparing them from the baseline model using the anova() function.<br>
(Intercept): Where everything is 0<br>
GROUP1: Is there a difference between group. If it is significant than there is a difference and the treatment had an effect.<br> 
WAVE: Asseses whether the effects gets bigger beteen time 2 and 3 (does not have to be significant)<br>
BASELINE: Should not be significant. If it is then it shows that there is a difference between groups before the treatment.<br>
GROUP1:WAVE: If this is significant then it means that the effect was either fleeting or it happened after the treatment i.e. between time 2 and 3. 
```{r}
summary(fullModeldata15)

```
Another random imputation
```{r}

data25=MI$imputations[[25]]

library("Zelig")
zelig.fitdata25 <- zelig(meanAPSI ~ GROUP * WAVE + BASELINE, random = ~1 | ID, data = data25,  model = "ls", cite = FALSE)
summary(zelig.fitdata25)
```
Describe the meanAPSI variable by the GROUP variable
```{r}
describeBy(data25[,3:4], group = data25$GROUP)
```
Create a plot that visualizes meanAPSI variable by the GROUP variable
```{r}
library(ggplot2)
library(influence.ME)
```
Take a look at the residuals
```{r}
residual <- lm(meanAPSI ~ BASELINE, data=data25)$residual
```
Plot the residuals to see that they are random
```{r}
plot(density(residual))# A density plot
qqnorm(residual) # A quantile normal plot to checking normality
qqline(residual)
```
Checking the different between intervention and control groups residuals. This allows us to control for individual unsystematic differences.  
```{r}
data2$residual <- NA
sel1 <- which(!is.na(data25$meanAPSI)) 
sel2 <- which(!is.na(data25$BASELINE))
data25$residual[intersect(sel1,sel2)] <- residual
qplot(GROUP, meanAPSI, data=data25, geom="boxplot")
```
Plot of the difference between intervention and control groups.
```{r}
qplot(GROUP, residual, data=data25, geom="boxplot")
```
Two way repeated measures
========================================================
Graphing the Two-Way Interaction. Both meanAPSI and the Residuals
```{r}
# Load the nlme package
library(nlme)
with(data25, boxplot(meanAPSI ~ WAVE + GROUP))
with(data25, boxplot(residual ~ WAVE + GROUP))
```
<center><font size="3" color="blue">Linear Mixed-Effects Model</font><center> Comparing Basline to Wave 2 and 3 by Group.
```{r}             
fullModeldata25 <- lme(meanAPSI ~ GROUP * WAVE + BASELINE, random = ~1 | ID, data = data25, method = "ML", na.action = "na.omit")
```
#Cooks Distence
```{r}
CookD(fullModeldata25)
```
#Plot Cook's distance:
```{r}
plot(fullModeldata25, which="cook")
```
Check results on this random Imputation model
<center><font size="6" color="green">Results</font><center>
<center><p><b>Explanation of significance:</b></p></center>
We asses the significance of our models by comparing them from the baseline model using the anova() function.<br>
(Intercept): Where everything is 0<br>
GROUP1: Is there a difference between group. If it is significant than there is a difference and the treatment had an effect.<br> 
WAVE: Asseses whether the effects gets bigger beteen time 2 and 3 (does not have to be significant)<br>
BASELINE: Should not be significant. If it is then it shows that there is a difference between groups before the treatment.<br>
GROUP1:WAVE: If this is significant then it means that the effect was either fleeting or it happened after the treatment i.e. between time 2 and 3. 
```{r}
summary(fullModeldata25)

```
Check assumptions on model without any imputations
```{r}

```
Describe the meanAPSI variable by the GROUP variable
```{r}
describeBy(data2[,3:4], group = data2$GROUP)
```
Create a plot that visualizes meanAPSI variable by the GROUP variable
```{r}
library(ggplot2)
library(influence.ME)
```
Take a look at the residuals
```{r}
residual <- lm(meanAPSI ~ BASELINE, data=data2)$residual
```
Plot the residuals to see that they are random
```{r}
plot(density(residual))# A density plot
qqnorm(residual) # A quantile normal plot to checking normality
qqline(residual)
```
Checking the different between intervention and control groups residuals. This allows us to control for individual unsystematic differences.  
```{r}
data2$residual <- NA
sel1 <- which(!is.na(data2$meanAPSI)) 
sel2 <- which(!is.na(data2$BASELINE))
data2$residual[intersect(sel1,sel2)] <- residual
qplot(GROUP, meanAPSI, data=data2, geom="boxplot")
```
Plot of the difference between intervention and control groups.
```{r}
qplot(GROUP, residual, data=data2, geom="boxplot")
```
Two way repeated measures
========================================================
Graphing the Two-Way Interaction. Both meanAPSI and the Residuals
```{r}
# Load the nlme package
library(nlme)
with(data2, boxplot(meanAPSI ~ WAVE + GROUP))
with(data2, boxplot(residual ~ WAVE + GROUP))
```
<center><font size="3" color="blue">Linear Mixed-Effects Model</font><center> Comparing Basline to Wave 2 and 3 by Group.
```{r}             
fullModel <- lme(meanAPSI ~ GROUP * WAVE + BASELINE, random = ~1 | ID, data = data2, method = "ML", na.action = "na.omit")
```
Table of full model with P-value
```{r, results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
out <- summary(fullModel)$tTable
kable(out, format = "markdown", padding = 2)
```
#Cooks Distence
```{r}
CookD(fullModel)
```
#Plot Cook's distance:
```{r}
plot(fullModel, which="cook")
```
Results on Model with data that contains no imputations
<center><font size="6" color="green">Results</font><center>
<center><p><b>Explanation of significance:</b></p></center>
We asses the significance of our models by comparing them from the baseline model using the anova() function.<br>
(Intercept): Where everything is 0<br>
GROUP1: Is there a difference between group. If it is significant than there is a difference and the treatment had an effect.<br> 
WAVE: Asseses whether the effects gets bigger beteen time 2 and 3 (does not have to be significant)<br>
BASELINE: Should not be significant. If it is then it shows that there is a difference between groups before the treatment.<br>
GROUP1:WAVE: If this is significant then it means that the effect was either fleeting or it happened after the treatment i.e. between time 2 and 3. 
```{r}
summary(fullModel)
library(knitr)
```
```{r, results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
out <- intervals(fullModel)$fixed
out1 <- summary(fullModel)$tTable
```
Table with confidence intervals without imputed data:

```{r, results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}

pandoc.table(out, split.table=100000)
```
Table with P-Value without imputed data:      

```{r, results = 'asis', echo=FALSE, message=FALSE, warning=FALSE}
pandoc.table(out1, split.table=100000)
