---
title: "EFA PWB"
author: "Levi Brackman"
date: "23 July 2015"
output: html_document
---


```{r}

##load packages
library(psych)
library(GPArotation)
library(plyr)
library(dplyr)

# data preparation
data <- read.csv("~/Psychometric_study_data/allsurveysT1.csv")
 PWB<-select(data,  PWB_1,  PWB_2,  PWB_3,  PWB_4,  PWB_5,  PWB_6, PWB_7,  PWB_8,  PWB_9)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
 PWB<- data.frame(apply(PWB,2, as.numeric))
 PWB<-tbl_df(PWB)
 PWB
str(PWB)
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
 PWB<- PWB[complete.cases(PWB[,]),]


##EFA
##number of factors
##parallal analysis and scree plot
parallel<-fa.parallel(PWB, fm="ml",fa="fa")
#two factors are greater than one Eigenvalue scree plot says there are two factors. Paralel analysis suggests 4 factors
#eigenvalues (kaiser)
parallel$fa.values
#over 1=2, over .7=2
#doign aprincipal components analysis to see how many factors there might be using that method
#Deal with NA doing principle componant analysis
princomp(na.omit(PWB), cor = TRUE)
parallel2<-princomp(na.omit(PWB), cor = TRUE)
summary(parallel2)
plot(parallel2)##results show at least two factors
#simple structure
twofactor<-fa(PWB, nfactors=2, rotate="oblimin", fm="ml")
twofactor
threefactor<-fa(PWB, nfactors=3, rotate="oblimin", fm="ml")
threefactor
fourfactor<-fa(PWB, nfactors=4, rotate="oblimin", fm="ml")
fourfactor
#question 1,3,5,6,9 seems to be one factor and all talk about plans or lack of plans
 PWBWO15<-select(PWB,  1,3,4,5,6,9)
 PWBWO15<-tbl_df(PWBWO15)
 PWBWO15
twofactorWO15<-fa(PWBWO15, nfactors=1, rotate="oblimin", fm="ml")
twofactorWO15
#CFI, should be slightly higher than the TLI
1-((twofactorWO15$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))
#question 7,8 seems to be one factor and all talk about being active or wondering aimlessly
 PWB78<-select(PWB,  7,8)
 PWB78<-tbl_df(PWB78)
 PWB78
twofactor78<-fa(PWB78, nfactors=1, rotate="oblimin", fm="ml")
twofactor78
#CFI, should be slightly higher than the TLI
1-((twofactorWO15$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))
#question 2,8 seems to be one factor 
 PWB29<-select(PWB, 2,8)
 PWB29<-tbl_df(PWB29)
 PWB29
twofactor29<-fa(PWB29, nfactors=1, rotate="oblimin", fm="ml")
twofactor29
#CFI, should be slightly higher than the TLI
1-((twofactor29$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))

##reliability
#alpha(PWB[,c(1,2,3,4,5,6,7,8,9)])
#alpha(PWB[,c(5,9,10,14)])
#What are the factors
#Factor 1 is positive emotions
#Factor 2 is negative emotions

#Create dataset for Target rotation
```{r}
all_surveys<-read.csv("allsurveysT1.csv")
PWB<-select(all_surveys, PWB_1, PWB_3, PWB_5,PWB_6, PWB_8,PWB_7, PWB_4, PWB_2, PWB_9)
PWB<- data.frame(apply(PWB,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

PWB<-tbl_df(PWB)
PWB
str(PWB)
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(9,list(f1=1:4,f2=5:7, f3=8:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(PWB,3,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
Droping question 4 because it loads on all of the factors. Much better fit to the data
```{r}
all_surveys<-read.csv("allsurveysT1.csv")
PWB<-select(all_surveys, PWB_1, PWB_3, PWB_5,PWB_6, PWB_8,PWB_7, PWB_2, PWB_9)
PWB<- data.frame(apply(PWB,2, as.numeric))
PWB<-tbl_df(PWB)
PWB
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(8,list(f1=1:4,f2=5:6, f3=7:8))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(PWB,3,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))

```
Droping question 1 as well because it also loads on all of the factors. Much better fit to the data
```{r}
all_surveys<-read.csv("allsurveysT1.csv")
PWB<-select(all_surveys, PWB_3, PWB_5,PWB_6, PWB_8,PWB_7, PWB_2, PWB_9)
PWB<- data.frame(apply(PWB,2, as.numeric))
PWB<-tbl_df(PWB)
PWB
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(7,list(f1=1:3,f2=4:5, f3=6:7))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(PWB,3,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
Adding a 4th factor with questions 1 and 4
```{r}
all_surveys<-read.csv("allsurveysT1.csv")
PWB<-select(all_surveys, PWB_3, PWB_5,PWB_6, PWB_8,PWB_7, PWB_2, PWB_9, PWB_1, PWB_4)
PWB<- data.frame(apply(PWB,2, as.numeric))
PWB<-tbl_df(PWB)
PWB
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(9,list(f1=1:3,f2=4:5, f3=6:7, f4=8:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
out_targetQ <- fa(PWB,4,rotate="TargetQ",Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))




