---
title: "EFA CFA & TR PWB Youth"
author: "Levi Brackman"
date: "25 January 2016"
output: html_document
---
1.	I live one day at a time and don't really think about the future. (rs)
2.	I tend to focus on the present, because the future always brings me problems. (rs)
3.	My daily activities often seem trivial and unimportant to me. (rs)
4.	I don't have a good sense of what it is that I am trying to accomplish in my life. (rs)
5.	I used to set goals for myself, but that now seems a waste of time. (rs)
6.	I enjoy making plans for the future and working to make them a reality. 
7.	I am an active person in carrying out the plans I set for myself. 
8.	Some people wander aimlessly through life, but I am not one of them. 
9.	I sometimes feel as if I’ve done all there is to do in life. (rs)


```{r}

##load packages
library(psych)
library(GPArotation)
library(plyr)
library(dplyr)

# data preparation
setwd("/Users/levibrackman/Documents/stats_march_2016/")
data <- read.csv("allsurveysYT1_Jan2016.csv", header=T)
PWB<-select(data,  PWB_1,  PWB_2,  PWB_3,  PWB_4,  PWB_5,  PWB_6, PWB_7,  PWB_8,  PWB_9)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
 PWB<- data.frame(apply(PWB,2, as.numeric))
 PWB<-tbl_df(PWB)
 PWB
str(PWB)
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
 PWB<- PWB[complete.cases(PWB[,]),]

#testing cronbach alpha in R
alpha(PWB, title=NULL, max=10,na.rm = TRUE, check.keys=TRUE,n.iter=1,delete=TRUE)
##EFA
##number of factors
##parallal analysis and scree plot
parallel<-fa.parallel(PWB, fm="ml",fa="fa")
#two factors are greater than one Eigenvalue scree plot says there are two factors. Paralel analysis suggests 4 factors
#eigenvalues (kaiser)
parallel$fa.values
#over 1=2, over .7=2
#doign aprincipal components analysis to see how many factors there might be using that method
#Deal with NA doing principle componant analysis
princomp(na.omit(PWB), cor = TRUE)
parallel2<-princomp(na.omit(PWB), cor = TRUE)
summary(parallel2)
plot(parallel2)##results show at least two factors
#simple structure
twofactor<-fa(PWB, nfactors=2, rotate="oblimin", fm="ml")
twofactor
#create table
Two_factor_Fits<-c(twofactor$STATISTIC, twofactor$PVAL, twofactor$dof, 1-((twofactor$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof)), twofactor$TLI, twofactor$RMSEA, twofactor$rms)
Two_factor_Fits<-as.data.frame(Two_factor_Fits)
require(reshape)
Two_factor_Fits <- melt(Two_factor_Fits, id.vars="Two_factor_Fits")

1-((twofactor$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))
fa2latex(fa(PWB,2, rotate="oblimin", fm="ml"),heading="Table 1. Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation of PWB-P")

threefactor<-fa(PWB, nfactors=3, rotate="oblimin", fm="ml")
#Creat Table
#Put all the fit measures together
Three_factor_Fits<-c(threefactor$STATISTIC, threefactor$PVAL, threefactor$dof, 1-((threefactor$STATISTIC - threefactor$dof)/(threefactor$null.chisq- threefactor$null.dof)), threefactor$TLI, threefactor$RMSEA, threefactor$rms)
#Make it as a dataframe
Three_factor_Fits<-as.data.frame(Three_factor_Fits)
require(reshape)
#Put into colunms
Three_factor_Fits <- melt(Three_factor_Fits, id.vars="Three_factor_Fits")
#CFI
1-((threefactor$STATISTIC - threefactor$dof)/(threefactor$null.chisq- threefactor$null.dof))

fa2latex(fa(PWB,3, rotate="oblimin", fm="ml"),heading="Table 3. Three Factor Loadings for Exploratory Factor Analysis with Oblimin Rotation of PWB-P")
fourfactor<-fa(PWB, nfactors=4, rotate="oblimin", fm="ml")
fourfactor
#question 1,3,5,6,9 seems to be one factor and all talk about plans or lack of plans
 PWBWO15<-select(PWB,  1,3,4,5,6,9)
 PWBWO15<-tbl_df(PWBWO15)
 PWBWO15
twofactorWO15<-fa(PWBWO15, nfactors=1, rotate="oblimin", fm="ml")
twofactorWO15
#CFI, should be slightly higher than the TLI
1-((twofactorWO15$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))
#question 7,8 seems to be one factor and all talk about being active or wondering aimlessly
 PWB78<-select(PWB,  7,8)
 PWB78<-tbl_df(PWB78)
 PWB78
twofactor78<-fa(PWB78, nfactors=1, rotate="oblimin", fm="ml")
twofactor78
#CFI, should be slightly higher than the TLI
1-((twofactorWO15$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))
#question 2,8 seems to be one factor 
 PWB29<-select(PWB, 2,8)
 PWB29<-tbl_df(PWB29)
 PWB29
twofactor29<-fa(PWB29, nfactors=1, rotate="oblimin", fm="ml")
twofactor29
#CFI, should be slightly higher than the TLI
1-((twofactor29$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))

##reliability
#alpha(PWB[,c(1,2,3,4,5,6,7,8,9)])
#alpha(PWB[,c(5,9,10,14)])
#What are the factors
#Factor 1 is positive emotions
#Factor 2 is negative emotions

#Create dataset for Target rotation
```{r}
all_surveys<-read.csv("allsurveysYT1_Jan2016.csv", header=T)
PWB<-select(all_surveys, PWB_1, PWB_2, PWB_3,PWB_4, PWB_5,PWB_6, PWB_7, PWB_8, PWB_9)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
PWB<- data.frame(apply(PWB,2, as.numeric))

```{r}
library(GPArotation)
library(psych)
library(dplyr)

PWB<-tbl_df(PWB)
PWB
str(PWB)
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(9,list(f1=1:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWB_cor <- corFiml(PWB) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWB_cor,1,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ

One_factor_Fits<-c(out_targetQ$STATISTIC, out_targetQ$PVAL, out_targetQ$dof, 1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof)), out_targetQ$TLI, out_targetQ$RMSEA, out_targetQ$rms)
One_factor_Fits<-as.data.frame(One_factor_Fits)
One_factor_Fits <- melt(One_factor_Fits, id.vars="One_factor_Fits")

```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```

#try something else 1,3,5,6 as factor one. 7 and 8 as factor 2. 2,4,9 as factor 3.
```{r}
all_surveys<-read.csv("allsurveysYT1_Jan2016.csv", header=T)
PWB<-select(all_surveys, PWB_1, PWB_3, PWB_5,PWB_6, PWB_7,PWB_8, PWB_2, PWB_4, PWB_9)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
PWB<- data.frame(apply(PWB,2, as.numeric))
Targ_key1 <- make.keys(9,list(f1=1:4,f2=5:6, f3=7:9))
Targ_key1 <- scrub(Targ_key1,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key1 <- list(Targ_key1)
PWB_cor1 <- corFiml(PWB) # convert the raw data to correlation matrix uisng FIML
out_targetQ1 <- fa(PWB_cor,3,rotate="TargetQ",n.obs = 1288,Target=Targ_key1) #TargetT for orthogonal rotation
out_targetQ1[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ1
#Create Table
ThreeTR_factor_Fits<-c(out_targetQ1$STATISTIC, out_targetQ1$PVAL, out_targetQ1$dof, 1-((out_targetQ1$STATISTIC - out_targetQ1$dof)/(out_targetQ1$null.chisq- out_targetQ1$null.dof)), out_targetQ1$TLI, out_targetQ1$RMSEA, out_targetQ1$rms)
ThreeTR_factor_Fits<-as.data.frame(ThreeTR_factor_Fits)
ThreeTR_factor_Fits <- melt(ThreeTR_factor_Fits, id.vars="ThreeTR_factor_Fits")
#Put all tables together
#Create List of names
namess<-c("Chisq", "P-Value", "DF", "CFI", "TLI", "RMSEA", "RMSEA ci upper", "RMSEA ci lower", "Confidence", "SRMR")
#Bind all colunms together
fitstable<-cbind(namess, One_factor_Fits, Two_factor_Fits, Three_factor_Fits, ThreeTR_factor_Fits)
fitstable<-select(fitstable, 'Models' = namess, 'One Factor' =  One_factor_Fits, 'Two Factors' = Two_factor_Fits, 'Three Factors' = Three_factor_Fits, 'Three Factors TR' = ThreeTR_factor_Fits)
fitstable<-fitstable[-9, ]
#Function to round number in dataframe
round_df <- function(df, digits) {
  nums <- vapply(df, is.numeric, FUN.VALUE = logical(1))

  df[,nums] <- round(df[,nums], digits = digits)

  (df)
}
#Round the numbers
fitstable<-round_df(fitstable, digits=3)
#Transpose the dataframe so that colunms end up being rows
fitstableT<-t(fitstable)
fitstableT<-as.data.frame(fitstableT)
#Create table
require(xtable)
xtable(fitstableT)

fa2latex(fa(PWB_cor,3,rotate="TargetQ", n.obs = 1288, Target=Targ_key), heading="Factor Loadings for Tarket Rotation, Three Factors")

#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
Droping question 4 because it loads on all of the factors. Much better fit to the data
```{r}
all_surveys<-read.csv("allsurveysYT1_Jan2016.csv", header=T)
PWB<-select(all_surveys, PWB_1, PWB_3, PWB_5,PWB_6, PWB_7,PWB_8, PWB_2, PWB_9)
PWB<- data.frame(apply(PWB,2, as.numeric))
PWB<-tbl_df(PWB)
PWB
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(8,list(f1=1:4,f2=5:7, f3=8))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWB_cor <- corFiml(PWB) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWB_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))

```
Droping question 1 as well because it also loads on all of the factors. Much better fit to the data
```{r}
all_surveys<-read.csv("allsurveysYT1_Jan2016.csv", header=T)
PWB<-select(all_surveys, PWB_3, PWB_5,PWB_6, PWB_8,PWB_7, PWB_2, PWB_9)
PWB<- data.frame(apply(PWB,2, as.numeric))
PWB<-tbl_df(PWB)
PWB
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(7,list(f1=1:3,f2=4:5, f3=6:7))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWB_cor <- corFiml(PWB) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWB_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
Adding a 4th factor with questions 1 and 4
```{r}
all_surveys<-read.csv("allsurveysT1.csv")
PWB<-select(all_surveys, PWB_3, PWB_5,PWB_6, PWB_8,PWB_7, PWB_2, PWB_9, PWB_1, PWB_4)
PWB<- data.frame(apply(PWB,2, as.numeric))
PWB<-tbl_df(PWB)
PWB
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(9,list(f1=1:3,f2=4:5, f3=6:7, f4=8:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWB_cor <- corFiml(PWB) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWB_cor,4,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))




