---
title: "PWB CFA TR Youth"
author: "Levi Brackman"
date: "26 January 2016"
output: html_document
---

1.	I live one day at a time and don't really think about the future. (rs)
2.	I tend to focus on the present, because the future always brings me problems. (rs)
3.	My daily activities often seem trivial and unimportant to me. (rs)
4.	I don't have a good sense of what it is that I am trying to accomplish in my life. (rs)
5.	I used to set goals for myself, but that now seems a waste of time. (rs)
6.	I enjoy making plans for the future and working to make them a reality. 
7.	I am an active person in carrying out the plans I set for myself. 
8.	Some people wander aimlessly through life, but I am not one of them. 
9.	I sometimes feel as if I've done all there is to do in life. (rs)

---

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
library(xtable) 
```
# data preparation
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
 PWB<-select(data,  PWB_1,  PWB_2,  PWB_3,  PWB_4,  PWB_5,  PWB_6, PWB_7,  PWB_8,  PWB_9)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
 PWB<- data.frame(apply(PWB,2, as.numeric))
str(PWB)
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
 PWB<- PWB[complete.cases(PWB[,]),]
```
##EFA
##number of factors
##parallal analysis and scree plot
```{r}
parallel<-fa.parallel(PWB, fm="ml",fa="fa")
#two factors are greater than one Eigenvalue scree plot says there are two factors. Paralel analysis suggests 4 factors
```
#eigenvalues (kaiser)
```{r}
parallel$fa.values
#over 1=2, over .7=2
```
#doign aprincipal components analysis to see how many factors there might be using that method
#Deal with NA doing principle componant analysis. 
```{r}
princomp(na.omit(PWB), cor = TRUE)
parallel2<-princomp(na.omit(PWB), cor = TRUE)
summary(parallel2)
plot(parallel2)##results show at least two factors
```
#simple structure
```{r}
twofactor<-fa(PWB, nfactors=2, rotate="oblimin", fm="ml")
twofactor
1-((twofactor$STATISTIC - twofactor$dof)/(twofactor$null.chisq- twofactor$null.dof))
fa2latex(fa(PWB,2,rotate="oblimin", fm="ml"), heading="Table 1. Factor Loadings for Exploratory Factor Analysis PWB")
threefactor<-fa(PWB, nfactors=3, rotate="oblimin", fm="ml")
threefactor
1-((threefactor$STATISTIC - threefactor$dof)/(threefactor$null.chisq- threefactor$null.dof))
fa2latex(fa(PWB,3,rotate="oblimin", fm="ml"), heading="Table 2. Factor Loadings for Exploratory Factor Analysis PWB")
fourfactor<-fa(PWB, nfactors=4, rotate="oblimin", fm="ml")
fourfactor
1-((fourfactor$STATISTIC - fourfactor$dof)/(fourfactor$null.chisq- fourfactor$null.dof))
fa2latex(fa(PWB,4,rotate="oblimin", fm="ml"), heading="Table 3. Factor Loadings for Exploratory Factor Analysis PWB")
```
#question 1,3,5,6,9 seems to be one factor and all talk about plans or lack of plans
```{r}
 PWBWO15<-select(PWB,  1,3,5,6,9)
 PWBWO15<-tbl_df(PWBWO15)
 PWBWO15
twofactorWO15<-fa(PWBWO15, nfactors=1, rotate="oblimin", fm="ml")
twofactorWO15
fa2latex(fa(PWBWO15,3,rotate="oblimin", fm="ml"), heading="Table 4. Factor Loadings for Exploratory Factor Analysis PWB")

```
#CFI, should be slightly higher than the TLI
```{r}
1-((twofactorWO15$STATISTIC - twofactorWO15$dof)/(twofactorWO15$null.chisq- twofactorWO15$null.dof))
```
#question 7,8 seems to be one factor and all talk about being active or wondering aimlessly
```{r}
 PWB78<-select(PWB,  7,8)
 PWB78<-tbl_df(PWB78)
 PWB78
twofactor78<-fa(PWB78, nfactors=1, rotate="oblimin", fm="ml")
twofactor78
fa2latex(fa(PWB78,1,rotate="oblimin", fm="ml"), heading="Table 5. Factor Loadings for Exploratory Factor Analysis PWB")

```
#CFI, should be slightly higher than the TLI
```{r}
1-((twofactor78$STATISTIC - twofactor78$dof)/(twofactor78$null.chisq- twofactor78$null.dof))
```
#question 2,8 seems to be one factor 
```{r}
 PWB29<-select(PWB, 2,8)
 PWB29<-tbl_df(PWB29)
 PWB29
twofactor29<-fa(PWB29, nfactors=1, rotate="oblimin", fm="ml")
twofactor29
fa2latex(fa(PWB29,1,rotate="oblimin", fm="ml"), heading="Table 6. Factor Loadings for Exploratory Factor Analysis PWB")

```
#CFI, should be slightly higher than the TLI
```{r}
1-((twofactor29$STATISTIC - twofactor29$dof)/(twofactor29$null.chisq- twofactor29$null.dof))
```
#Finding Alpha
```{r}
#alpha(PWB, na.rm = TRUE, check.keys=TRUE)
```
#CFA in Lavaan
```{r}
data <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
data<-tbl_df(data)
PWB<-select(data, PWB_1, PWB_2, PWB_3, PWB_4, PWB_5, PWB_6,PWB_7, PWB_8, PWB_9)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
PWB<-tbl_df(PWB)
PWB

```
#create plots
```{r}
#ggpairs(PWB, columns = 1:15, title="Big 5 Marsh" )

```
#create the models
```{r}
two.model= ' Factor1  =~ PWB_1 +  PWB_3  + PWB_4 + PWB_5 + PWB_6 + PWB_9   
              Factor2 =~   PWB_2+ PWB_7 + PWB_8
'  #Models two factors:Positive and Negative     
              

one.model= 'PWB =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_6 + PWB_7 + PWB_8 + PWB_9' #Models as a single purpose factor
```
Second order models
```{r}

second.model = '  Negative  =~  PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_9 
                Positive =~   PWB_6 + PWB_7 + PWB_8
                Purpose =~ Negative + Positive 
' #Second order models as Purpose being the higher factor made up of Purpose and Positive

```
Bifactor (like model 7 in Marsh, Scalas & Nagengast, 2010)
```{r}

bifactor.negative.model = 'Negative =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_9  
                                     PWB =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_6 + PWB_7 + PWB_8 + PWB_9 
'
#Models bifactor as the negatively worded item as a factor uncorolated with the main factor


bifactor.model1 = 'PWB =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_6 + PWB_7 + PWB_8 + PWB_9
                Negative  =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_9   
              Positive =~   PWB_6 + PWB_7 + PWB_8
                PWB ~~ 0*Negative
                PWB ~~ 0*Positive
                Negative~~0*Positive
'#Models bifactor with Positive and Purpose as factors uncorolated with the main factor

bifactor.model2 = 'PWB =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_6 + PWB_7 + PWB_8 + PWB_9
                F1  =~ PWB_1 +  PWB_3  + PWB_5 + PWB_6   
                F2 =~   PWB_4 + PWB_7 + PWB_8 
                F3 =~ PWB_2 + PWB_9 
                PWB ~~ 0*F1
                PWB ~~ 0*F2
                PWB ~~ 0*F3
                F1~~0*F2
                F1~~0*F3
                F2~~0*F3
'#Models bifactor with Positive and Purpose as factors uncorolated with the main factor

```
#run the models
```{r}
two.fit=cfa(two.model, data=PWB, missing = "fiml", std.lv = T)
one.fit=cfa(one.model, data=PWB, missing = "fiml", std.lv = T)
second.fit=cfa(second.model, data=PWB, missing = "fiml", std.lv = T)
bifactor1.fit=cfa(bifactor.model1, data=PWB, missing = "fiml", std.lv = T)
bifactor2.fit=cfa(bifactor.model2, data=PWB, missing = "fiml", std.lv = T)
bifactorneg.fit = cfa(bifactor.negative.model, data=PWB, missing = "fiml", std.lv = T)
bifactor.negative.fit=cfa(bifactor.negative.model, data=PWB, missing = "fiml", std.lv = T)
```

#create pictures
```{r}
semPaths(two.fit, whatLabels = "std", layout = "tree")
semPaths(two.fit, intercepts = FALSE, residual = FALSE, layout = "tree2", sizeMan = 4, font = 3,
         sizeLat=4.3, bifactor = "Purpose",edge.color="black", nCharNodes = 6, mar = c(3, 1,3, 1))
semPaths(one.fit, whatLabels = "std", layout = "tree")
semPaths(one.fit, intercepts = FALSE, residual = FALSE, layout = "tree2", sizeMan = 4, font = 3,
         sizeLat=4.3, bifactor = "Purpose",edge.color="black", nCharNodes = 6, mar = c(3, 1,3, 1))
semPaths(second.fit, whatLabels = "std", layout = "tree")
semPaths(second.fit, intercepts = FALSE, residual = FALSE, layout = "tree2", sizeMan = 4, font = 3,
         sizeLat=4.3, bifactor = "Purpose",edge.color="black", nCharNodes = 6, mar = c(3, 1,3, 1))
semPaths(bifactor1.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor1.fit, intercepts = FALSE, residual = FALSE, layout = "tree2", sizeMan = 5, font = 3,
         sizeLat=4.3, bifactor = "Purpose",edge.color="black", nCharNodes = 6, mar = c(3, 1,3, 1))
semPaths(bifactor2.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor2.fit, intercepts = FALSE, residual = FALSE, layout = "tree2", sizeMan = 4, font = 3,
         sizeLat=4.3, bifactor = "Purpose",edge.color="black", nCharNodes = 6, mar = c(3, 1,3, 1))
semPaths(bifactorneg.fit, whatLabels = "std", layout = "tree")
semPaths(bifactorneg.fit, intercepts = FALSE, residual = FALSE, layout = "tree2", sizeMan = 4, font = 3,
         sizeLat=4.3, bifactor = "Purpose",edge.color="black", nCharNodes = 6, mar = c(3, 1,3, 1))

```
#summaries
```{r}
summary(two.fit, standardized = TRUE, rsquare=TRUE)
(xtable(parameterEstimates(two.fit, ci = F, standardized = T,  fmi = F, remove.eq = F, 
                   remove.ineq = F, remove.def = T)))
summary(one.fit, standardized = TRUE, rsquare=TRUE)
(xtable(parameterEstimates(one.fit, ci = F, standardized = T,  fmi = F, remove.eq = F, 
                   remove.ineq = F, remove.def = T)))
summary(second.fit, standardized = TRUE, rsquare=TRUE)
(xtable(parameterEstimates(second.fit, ci = F, standardized = T,  fmi = F, remove.eq = F, 
                   remove.ineq = F, remove.def = T)))
summary(bifactor1.fit, standardized = TRUE, rsquare=TRUE)
(xtable(parameterEstimates(bifactor1.fit, ci = F, standardized = T,  fmi = F, remove.eq = F, 
                   remove.ineq = F, remove.def = T)))
summary(bifactor2.fit, standardized = TRUE, rsquare=TRUE)
(xtable(parameterEstimates(bifactor2.fit, ci = F, standardized = T,  fmi = F, remove.eq = F, 
                   remove.ineq = F, remove.def = T)))
summary(bifactor.negative.fit, standardized = TRUE, rsquare=TRUE)
(xtable(parameterEstimates(bifactor.negative.fit, ci = F, standardized = T,  fmi = F, remove.eq = F, 
                   remove.ineq = F, remove.def = T)))
?parameterEstimates
```
#Residual correlations
```{r}
correl = residuals(two.fit, type="cor")
correl
View(correl$cor)
correl1 = residuals(one.fit, type="cor")
correl1
View(correl1$cor)
correl0 = residuals(second.fit, type="cor")
correl0
View(correl0$cor)
correl4 = residuals(bifactor1.fit, type="cor")
correl4
View(correl4$cor)
correl5 = residuals(bifactor2.fit, type="cor")
correl5
correl3 = residuals(bifactor.negative.fit, type="cor")
correl3
View(correl3$cor)
```
#Modification indicies
```{r}
#modindices(two.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(one.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor1.fit, sort. = TRUE, minimum.value = 3.84)
#modindices(bifactor.negative.fit, sort. = TRUE, minimum.value = 3.84)
```
#Fit Measures
```{r}
fitmeasures(two.fit)#Models two factors:Positive and Negative for Purpose  
fitmeasures(one.fit) #Models as a single purpose factor
fitmeasures(second.fit)#Second order models as Purpose being the higher factor made up of Purpose and Positive
fitmeasures(bifactor1.fit)#Models bifactor with Positive and Purpose as factors uncorolated with the main factor
fitmeasures(bifactor2.fit)#Models bifactor with Positive and Purpose as factors uncorolated with the main factor
fitmeasures(bifactor.negative.fit)#Models bifactor as the negatively worded item as a factor uncorolated with the main factor
```
#Create dataset for Target rotation
```{r}
all_surveys <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
PWBTR<-select(all_surveys, PWB_1, PWB_2, PWB_3,PWB_4, PWB_5,PWB_6,PWB_9, PWB_8,PWB_7)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
PWBTR<- data.frame(apply(PWBTR,2, as.numeric))

library(GPArotation)
library(psych)
library(dplyr)

PWBTR<-tbl_df(PWBTR)
PWBTR
str(PWBTR)
colnames(PWBTR) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(9,list(f1=1:6,f2=7:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWBTR_cor <- corFiml(PWBTR) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWBTR_cor,2,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
fa2latex(fa(PWBTR_cor,2,rotate="TargetQ",n.obs = 816,Target=Targ_key), heading="Table 7. Factor Loadings for Exploratory Factor Analysis PWB")
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))

```
#Target toration as three factors based on EFA - works well as three factors but with cross loadings
```{r}
all_surveys <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
PWBTR<-select(all_surveys, PWB_1, PWB_3, PWB_5,PWB_6, PWB_7, PWB_4,PWB_8, PWB_2,PWB_9)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
PWBTR<- data.frame(apply(PWBTR,2, as.numeric))

library(GPArotation)
library(psych)
library(dplyr)

PWBTR<-tbl_df(PWBTR)
PWBTR
str(PWBTR)
colnames(PWBTR) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(9,list(f1=1:4,f2=5:6, f3=7:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWBTR_cor <- corFiml(PWBTR) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWBTR_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
fa2latex(fa(PWBTR_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key), heading="Table 8. Factor Loadings for Exploratory Factor Analysis PWB")
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
#Create dataset for Target rotation
```{r}
all_surveys <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
PWB<-select(all_surveys, PWB_1, PWB_3, PWB_5,PWB_6, PWB_7, PWB_8,   PWB_2, PWB_4, PWB_9)
PWB<- data.frame(apply(PWB,2, as.numeric))


library(GPArotation)
library(psych)
library(dplyr)

PWB<-tbl_df(PWB)
PWB
str(PWB)
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(9,list(f1=1:4,f2=5:7, f3=8:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWB_cor <- corFiml(PWB) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWB_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
fa2latex(fa(PWB_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key), heading="Table 9. Factor Loadings for Exploratory Factor Analysis PWB")
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
Based on the above model we try F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9. this the best fit to the data. (PWB_4 crossloads)
```{r}
all_surveys <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
PWB<-select(all_surveys, PWB_1, PWB_3, PWB_5,PWB_6, PWB_7, PWB_8,PWB_4, PWB_2,  PWB_9)
PWB<- data.frame(apply(PWB,2, as.numeric))
PWB<-tbl_df(PWB)
PWB
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(9,list(f1=1:4,f2=5:7, f3=8:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWB_cor <- corFiml(PWB) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWB_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
fa2latex(fa(PWB_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key), heading="Table 10. Factor Loadings for Exploratory Factor Analysis PWB")
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
```
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```{r}
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))

```
Droping question 1 as well because it also loads on all of the factors. Much better fit to the data
```{r}
all_surveys <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
PWB<-select(all_surveys, PWB_3, PWB_5,PWB_6, PWB_8,PWB_7, PWB_2, PWB_9)
PWB<- data.frame(apply(PWB,2, as.numeric))
PWB<-tbl_df(PWB)
PWB
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(7,list(f1=1:3,f2=4:5, f3=6:7))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWB_cor <- corFiml(PWB) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWB_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
fa2latex(fa(PWB_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key), heading="Table 11. Factor Loadings for Exploratory Factor Analysis PWB")
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))
```
Dropping PWB_4 -- still not great and PWB_1 crossloads significantly and PWB_9 does not load well on any of the factors.
```{r}
all_surveys <- read.csv("~/Dropbox/Git/stats/allsurveysYT1_Jan2016.csv", header=T)
PWB<-select(all_surveys, PWB_1, PWB_3, PWB_5,PWB_6, PWB_7, PWB_8, PWB_2,  PWB_9)
PWB<- data.frame(apply(PWB,2, as.numeric))
PWB<-tbl_df(PWB)
PWB
colnames(PWB) <- c("1","2", "3", "4", "5", "6", "7", "8")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(8,list(f1=1:4,f2=5:6, f3=7:8))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWB_cor <- corFiml(PWB) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWB_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
fa2latex(fa(PWB_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key), heading="Table 12. Factor Loadings for Exploratory Factor Analysis PWB")
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
#The best fit to the data seems to be three factors. F1: questions 1,3,5,6. f2: 8,7,4. f3: 2,9
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))

