---
title: "PWB CFA TR Youth"
author: "Levi Brackman"
date: "28 July 2015"
output: html_document
---

1.	I live one day at a time and don't really think about the future. (rs)
2.	I tend to focus on the present, because the future always brings me problems. (rs)
3.	My daily activities often seem trivial and unimportant to me. (rs)
4.	I don't have a good sense of what it is that I am trying to accomplish in my life. (rs)
5.	I used to set goals for myself, but that now seems a waste of time. (rs)
6.	I enjoy making plans for the future and working to make them a reality. 
7.	I am an active person in carrying out the plans I set for myself. 
8.	Some people wander aimlessly through life, but I am not one of them. 
9.	I sometimes feel as if I've done all there is to do in life. (rs)

---

```{r}
library(lavaan)
library(semPlot)
library(dplyr)
library(GPArotation)
library(psych)
library(car)
library(ggplot2)
library(GGally)
```
#loadthedata
```{r}
setwd("/Users/levibrackman/Documents/stats_march_2016/")
data <- read.csv("allsurveysYT1_Jan2016.csv", header=T)
data<-tbl_df(data)
PWB<-select(data, PWB_1, PWB_2, PWB_3, PWB_4, PWB_5, PWB_6,PWB_7, PWB_8, PWB_9)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
PWB<-tbl_df(PWB)
PWB

```
#create plots
```{r}
#ggpairs(PWB, columns = 1:15, title="Big 5 Marsh" )

```
#create the models
```{r}
two.model= ' Factor1  =~ PWB_1 +  PWB_3  + PWB_4 + PWB_5 + PWB_6 + PWB_9   
              Factor2 =~   PWB_2+ PWB_7 + PWB_8
'  #Models two factors:Positive and Negative     

three.model= ' F1  =~ PWB_1 +  PWB_3  + PWB_5 + PWB_6   
                F2 =~    PWB_7 + PWB_8 
                F3 =~ PWB_2 + PWB_9 + PWB_4'

#Models three factors based on EFA 

one.model= 'PWB =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_6 + PWB_7 + PWB_8 + PWB_9' #Models as a single purpose factor
```
Second order models
```{r}

second.model = '  F1  =~ PWB_1 +  PWB_3  + PWB_5 + PWB_6   
                F2 =~    PWB_7 + PWB_8 
                F3 =~ PWB_2 + PWB_9 + PWB_4
                HO =~ F1+F2+F3'
                F3 ~~ 0*F3'
 #Second order models as Purpose being the higher factor made up of Purpose and Positive
second.modelWOF2 = '  F1  =~ PWB_1 +  PWB_3  + PWB_5 + PWB_6   
                F3 =~ PWB_2 + PWB_9 + PWB_4
                HO =~ F1+F3
                F1 ~~ 0*F1
' #Second order models as Purpose being the higher factor made up of Purpose and Positive
```
Bifactor (like model 7 in Marsh, Scalas & Nagengast, 2010)
```{r}

bifactor.negative.model = 'Negative =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_9  
                                     PWB =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_6 + PWB_7 + PWB_8 + PWB_9 
'#Models bifactor as the negatively worded item as a factor uncorolated with the main factor

bifactor.model1 = 'PWB =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_6 + PWB_7 + PWB_8 + PWB_9
                F1  =~ PWB_1 +  PWB_3  + PWB_5 + PWB_6   
                F2 =~    PWB_7 + PWB_8 
                F3 =~ PWB_2 + PWB_9 + PWB_4
                F1 ~~ 0*F1
'#Models bifactor with Positive and Purpose as factors uncorolated with the main factor

bifactor.model2 = 'PWB =~ PWB_1 +  PWB_2  + PWB_3 + PWB_4 + PWB_5 + PWB_6 + PWB_7 + PWB_8 + PWB_9
                F1  =~ PWB_1 +  PWB_3  + PWB_5 + PWB_6   
                F2 =~   PWB_4 + PWB_7 + PWB_8 
                F3 =~ PWB_2 + PWB_9 
                PWB ~~ 0*F1
                PWB ~~ 0*F2
                PWB ~~ 0*F3
                F1~~0*F2
                F1~~0*F3
                F2~~0*F3
'#Models bifactor with Positive and Purpose as factors uncorolated with the main factor

```
#run the models
```{r}
three.fit=cfa(three.model, data=PWB, missing = "fiml", std.lv = T)
one.fit=cfa(one.model, data=PWB, missing = "fiml", std.lv = T)
second.fit=cfa(second.model, data=PWB, missing = "fiml", std.lv = T)
inspect(second.fit,"cov.lv")
eigen(inspect(second.fit, "cov.lv"))$values
inspect(second.fit, "theta")
second.fitWOF2=cfa(second.modelWOF2, data=PWB, missing = "fiml", std.lv = F)
bifactor1.fit=cfa(bifactor.model1, data=PWB, missing = "fiml", std.lv = T)
bifactor2.fit=cfa(bifactor.model2, data=PWB, missing = "fiml", std.lv = T)
bifactor.negative.fit=cfa(bifactor.negative.model, data=PWB, missing = "fiml", std.lv = T)
```

#create pictures
```{r}
semPaths(two.fit, whatLabels = "std", layout = "tree")
semPaths(three.fit, whatLabels = "std", layout = "tree")
semPaths(second.fit, whatLabels = "std", layout = "tree")
semPaths(second.fitWOF2, whatLabels = "std", layout = "tree")

semPaths(bifactor1.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor2.fit, whatLabels = "std", layout = "tree")
semPaths(bifactor.negative.fit, whatLabels = "std", layout = "tree")
```
#summaries
```{r}
summary(two.fit, standardized = TRUE, rsquare=TRUE)
summary(three.fit, standardized = TRUE, rsquare=TRUE)
summary(second.fit, standardized = TRUE, rsquare=TRUE)
summary(second.fitWOF2, standardized = TRUE, rsquare=TRUE)

summary(bifactor1.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor2.fit, standardized = TRUE, rsquare=TRUE)
summary(bifactor.negative.fit, standardized = TRUE, rsquare=TRUE)
```
#Residual correlations
```{r}
correl = residuals(two.fit, type="cor")
correl
View(correl$cor)
correl1 = residuals(three.fit, type="normalized")
correl1
View(correl1$cor)
correl0 = residuals(second.fit, type="standardized")
correl0
correl4 = residuals(second.fitWOF2, type="standardized")
correl4
#over 1.96 is statistically significant
View(correl0$cor)
correl4 = residuals(bifactor1.fit, type="cor")
correl4
View(correl4$cor)
correl5 = residuals(bifactor2.fit, type="cor")
correl5
correl3 = residuals(bifactor.negative.fit, type="cor")
correl3
View(correl3$cor)
```
#Modification indicies
```{r}
modindices(two.fit, sort. = TRUE, minimum.value = 3.84)
modindices(three.fit, sort. = TRUE, minimum.value = 3.84)
modindices(bifactor1.fit, sort. = TRUE, minimum.value = 3.84)
modindices(second.fit, sort. = TRUE, minimum.value = 3.84)

#modindices(bifactor.negative.fit, sort. = TRUE, minimum.value = 3.84)
```
#Fit Measures
```{r}
#fitmeasures(two.fit)#Models three  
threefactorfit<-fitmeasures(three.fit,  c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr")) 
threefactorfit 
secondorderfit<-fitmeasures(second.fit,  c("chisq", "df", "pvalue", "cfi", "tli", "rmsea", "rmsea.ci.lower", "rmsea.ci.upper", "srmr"))
secondorderfit
#Second order models as Purpose being the higher factor made up of Purpose and Positive
fitmeasures(second.fitWOF2)#Second order models as Purpose being the higher factor made up of Purpose and Positive

fitmeasures(bifactor1.fit)#Models bifactor with Positive and Purpose as factors uncorolated with the main factor
fitmeasures(bifactor2.fit)#Models bifactor with Positive and Purpose as factors uncorolated with the main factor
fitmeasures(bifactor.negative.fit)#Models bifactor as the negatively worded item as a factor uncorolated with the main factor
```
#Tables
```{r}
tabel.threefit<-parameterEstimates(three.fit, zstat = F, pvalue = F, ci = F, 
                   level = 0.95, boot.ci.type = "perc", standardized = T, 
                   fmi = F, remove.system.eq = TRUE, remove.eq = TRUE, 
                   remove.ineq = TRUE, remove.def = T, rsquare = FALSE, 
                   add.attributes = FALSE)
tabel.threefit<-select(tabel.threefit, "Factor Names" = lhs, Items = rhs, Loadings = std.all)
tabel.threefit<-tabel.threefit[c(1:9), ]
#second order table
tabel.secondorderfit<-parameterEstimates(second.fit, zstat = F, pvalue = F, ci = F, 
                   level = 0.95, boot.ci.type = "perc", standardized = T, 
                   fmi = F, remove.system.eq = TRUE, remove.eq = TRUE, 
                   remove.ineq = TRUE, remove.def = T, rsquare = FALSE, 
                   add.attributes = FALSE)
tabel.secondorderfit<-select(tabel.secondorderfit, "Factor Names" = lhs, Items = rhs, Loadings = std.all)
tabel.secondorderfit<-tabel.secondorderfit[(1:12), ]

all_fits_table<-rbind(tabel.threefit, tabel.secondorderfit)
#change order of colunms
all_fits_table$Models      <- ""
all_fits_table <- all_fits_table[c(4,2,1,3)]
print(xtable(all_fits_table, caption = 'Factor Loadings for Confirmatory Factor Analysis with Lavaan of Three Factor and Second Order for PWB', table.placement =""))

```
Creat tables of fit meansure
```{r}
namess<-c("Chisq", "DF", "P-Value", "CFI", "TLI", "RMSEA", "RMSEA ci upper", "RMSEA ci lower", "SRMR")
namess<-as.data.frame(namess)
threefactorfit<-data.frame(threefactorfit)
secondorderfit<-data.frame(secondorderfit)
all<-bind_cols(namess, threefactorfit, secondorderfit)
require(dplyr)
tableall_fit_measures<-select(all, 'Fit Measures' = namess, 'Three Factor Model' =  threefactorfit, 'Second Order Model' = secondorderfit)
round_df <- function(df, digits) {
  nums <- vapply(df, is.numeric, FUN.VALUE = logical(1))

  df[,nums] <- round(df[,nums], digits = digits)

  (df)
}
#Round the numbers
tableall_fit_measures<-round_df(tableall_fit_measures, digits=3)
#Transpose the dataframe so that colunms end up being rows
tableall_fit_measures<-t(tableall_fit_measures)
tableall_fit_measures<-as.data.frame(tableall_fit_measures)
#Create table
require(xtable)
xtable(tableall_fit_measures)
tableall_fit_measures



```
#Create dataset for Target rotation
```{r}
all_surveys<-read.csv("allsurveysYT1.csv")
PWBTR<-select(all_surveys, PWB_1, PWB_2, PWB_3,PWB_4, PWB_5,PWB_6,PWB_9, PWB_8,PWB_7)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
PWBTR<- data.frame(apply(PWBTR,2, as.numeric))

library(GPArotation)
library(psych)
library(dplyr)

PWBTR<-tbl_df(PWBTR)
PWBTR
str(PWBTR)
colnames(PWBTR) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(9,list(f1=1:6,f2=7:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWBTR_cor <- corFiml(PWBTR) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWBTR_cor,2,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))

```
#Target toration as three factors - works well as three factors but with cross loadings
```{r}
all_surveys<-read.csv("allsurveysYT1.csv")
PWBTR<-select(all_surveys, PWB_1, PWB_3, PWB_5,PWB_6, PWB_4,PWB_7,PWB_8, PWB_2,PWB_9)
PWB$PWB_1  <-  7- PWB$PWB_1
PWB$PWB_2  <-  7- PWB$PWB_2
PWB$PWB_3  <-  7- PWB$PWB_3
PWB$PWB_4  <-  7- PWB$PWB_4
PWB$PWB_9  <-  7- PWB$PWB_9
PWBTR<- data.frame(apply(PWBTR,2, as.numeric))

library(GPArotation)
library(psych)
library(dplyr)

PWBTR<-tbl_df(PWBTR)
PWBTR
str(PWBTR)
colnames(PWBTR) <- c("1","2", "3", "4", "5", "6", "7", "8", "9")
#Target rotation: choose "simple structure" a priori and can be applied to oblique and orthogonal rotation based on 
#what paper says facotrs should be PWB
Targ_key <- make.keys(9,list(f1=1:4,f2=5:7, f3=8:9))
Targ_key <- scrub(Targ_key,isvalue=1)  #fix the 0s, allow the NAs to be estimated
Targ_key <- list(Targ_key)
PWBTR_cor <- corFiml(PWBTR) # convert the raw data to correlation matrix uisng FIML
out_targetQ <- fa(PWBTR_cor,3,rotate="TargetQ",n.obs = 816,Target=Targ_key) #TargetT for orthogonal rotation
out_targetQ[c("loadings", "score.cor", "TLI", "RMSEA")]
out_targetQ
```
CFI
```{r}
1-((out_targetQ$STATISTIC - out_targetQ$dof)/(out_targetQ$null.chisq- out_targetQ$null.dof))



